\documentclass[noauthor,nooutcomes,12pt,handout,hints]{ximera}

\input{../preamble.tex}

\title{Arccosine} \author{Bart Snapp}

\begin{document}
\begin{abstract}
  Arccosine tells us the arc covered by an angle based on the value of
  cosine.
\end{abstract}
\maketitle

\begin{listOutcomes}
\item Understand that arccosine accepts a ratio of sides as input, and
  outputs the measure of an angle.
\item Understand that arccosine is the inverse function of cosine for
  angles between $0$ and $180$ degrees.
\item Recognize when arccosine and cosine undo each other, and also
  when they do not undo each other.
\end{listOutcomes}
\mynewpage




\begin{question}
  Here is a table of cosine and arccosine values:
  \[
  \begin{array}{|l|l|} \hline
    \cos(\theta)  = x     & \arccos(x) = \theta \\ \hline\hline
    \cos(0)  = 1     & \arccos(1) = 0 \\ \hline
    \cos(30) = 0.866 & \arccos(0.866) = 30\\ \hline
    \cos(60) = 0.5 & \arccos(0.5) = 60\\ \hline
    \cos(90) = 0 & \arccos(0) = 90\\ \hline
    \cos(120) = -0.5 & \arccos(-0.5) = 120\\ \hline
    \cos(150) = -0.866 & \arccos(-0.866) = 150\\ \hline
    \cos(180) =-1 & \arccos(-1) = 180  \\\hline
  \end{array}
  \]
  Explain what arccosine does when $0^\circ \le \theta \le 180^\circ$
  and $-1\le x\le 1$, as based on the table above.
  \begin{freeResponse}
    If you have an angle between $0^\circ$ and $180^\circ$ and $-1\le
    x\le 1$, then arccosine ``undoes'' cosine and vice versa. So if
    $0^\circ \le \theta \le 180^\circ$ and $-1\le x\le 1$,
    \[
    \cos(\arccos(x)) = x\qquad\text{and}\qquad \arccos(\cos(\theta)) =
    \theta.
    \]
  \end{freeResponse}
\end{question}
\mynewpage



\begin{question}
  Here are more values of cosine and arccosine:
  \[
  \begin{array}{|l|l|}
    \hline
    \cos(\theta) =x      & \arccos(x) = \theta\\ \hline\hline
    \cos(180) =-1      & \arccos(-1) = 180\\ \hline
    \cos(210) = -0.866 & \arccos(-0.866) = 150\\ \hline
    \cos(240) = -0.5   & \arccos(-0.5) = 120\\ \hline
    \cos(270) = 0      & \arccos(0) = 90\\ \hline
    \cos(300) = 0.5     & \arccos(0.5) = 60\\ \hline
    \cos(330) = 0.866   & \arccos(0.866) = 30\\ \hline
    \cos(360)  = 1     & \arccos(1) = 0 \\    \hline
  \end{array}
  \]
  Use the information from problem 1 and 2 to enhance your answer from
  problem 1. That is EXPLAIN what arccosine does when $180^\circ \le
  \theta \le 360^\circ$ and $-1\le x\le 1$, as based on the table
  above.
  \begin{freeResponse}
    If you have an angle $\theta$ between $180^\circ$ and $360^\circ$
    and $-1\le x\le 1$, then cosine still undoes arccosine,
    \[
    \cos(\arccos(x)) = x
    \]
    BUT arccosine no longer undoes ``cosine.'' Instead in this case
    \[
    \arccos(\cos(\theta)) = 360-\theta.
    \]
  \end{freeResponse}
\end{question}
\mynewpage



\begin{question}
  One of the following statements is TRUE, the other is FALSE,
  \[
  \cos(\arccos(x)) = x \qquad \text{or} \qquad \arccos(\cos(\theta))
  =\theta.
  \]
  EXPLAIN:
  \begin{enumerate}
  \item WHY we use two different letters, $x$ and $\theta$. In
    particular, explain what $x$ and $\theta$ represent.
  \item WHY the true statement is true.
  \item WHY the false statement is false.
  \end{enumerate}
  Use words, pictures, examples, and so on, as needed/helpful in your
  explanations.
  \begin{freeResponse}
    \begin{enumerate}
    \item We use two different letters because they represent
      different things.
      \begin{align*}
        \theta &= \text{an angle},\\
        x &=\text{a number between $-1$ and $1$}.
      \end{align*}
    \item The TRUE statement is:
      \[
      \cos(\arccos(x)) = x
      \]
      This is always true, because:
      \begin{center}
        \begin{tikzpicture} 
          \node[anchor=east,rounded corners=5pt,draw] at (0,0) {$-1\le x\le 1$};
          \draw [->,thick] (.2,.5) to [out=30,in=150] (2.8,.5);
          \node[anchor=west,rounded corners=5pt,draw] at (3,0) {$0^\circ\le \theta\le 180^\circ$};
          \draw [->,thick] (2.8,-.5) to [out=-150,in=-30] (.2,-.5);
          \node at (1.5,1.2) {$\arccos$};
          \node at (1.5,-1.2) {$\cos$};
        \end{tikzpicture}
      \end{center}
      Arccosine turns ratios between $-1$ and $1$ into angles, then
      cosine sends these angles back to the ratios.
    \item The FALSE statement is:
      \[
      \arccos(\cos(\theta)) = \theta
      \]
      This is false if $\theta$ is not between $0^\circ$ and
      $180^\circ$, because:
      \begin{center}
        \begin{tikzpicture} 
          \node[anchor=east,rounded corners=5pt,draw] at (0,0) {$180^\circ\le \theta\le 360^\circ$};
          \draw [->,thick] (.2,0) to  (2.8,0);
          \node[anchor=west,rounded corners=5pt,draw] at (3,0) {$-1\le x\le 1$};
          \draw [->,thick] (5.65,0) to  (8.25,0);
          \node[anchor=west,rounded corners=5pt,draw] at (8.45,0) {$0^\circ\le \theta\le 180^\circ$};
          \node at (1.5,.5) {$\cos$};
          \node at (6.95,.5) {$\arccos$};
        \end{tikzpicture}
      \end{center}
      Cosine turns angles (even those outside the range of $0^\circ$
      to $180^\circ$) into ratios between $-1$ and $1$. Arccosine
      turns these into angles between $0^\circ$ and $180^\circ$. If
      you start with an angle $\theta$ outside of this range, $\arccos(\cos(\theta)) \neq \theta$.
      
    \end{enumerate}
  \end{freeResponse}
\end{question}



\end{document}
