\documentclass{ximera}

\input{../preamble.tex}

\outcome{State a physical property of triangles.}
\outcome{State the triangle congruence theorems.}
\outcome{Identify situations where congruence theorems apply.}
\outcome{Use a congruence theorem to explain why a triangle is a rigid shape.}

\title{Why triangles?}
\author{Bart Snapp}

\begin{document}
\begin{abstract}
  We seek to understand the importance of triangles and the triangle
  congruence theorems.
\end{abstract}
\maketitle


\theoutcomes



\begin{question}
  Someone once told me,
  \begin{quote}
    \textit{a triangle is the strongest shape.}
  \end{quote}
  Explain what they meant by this.
  \begin{freeResponse}
    They mean if you want to build a rigid structure, with a frame,
    then using triangles in your structure will make your structure
    strong. This strength will remain even if there is some play
    or wiggle in the joints.
  \end{freeResponse}
\end{question}

\begin{question}
  Use the INTERNET or a LIBRARY to look up the \textit{triangle congruence
  theorems: SSS, SAS, ASA, AAS.}


  EXPLAIN the statements of these theorems as you would like to have
  them explained to you. Use words, pictures, and so on, as
  needed/helpful in your explanation.

  Finally, give an example of a trio of either S's or A's that is NOT
  a congruence theorem, and EXPLAIN using words, pictures, and so on,
  WHY this is not a congruence theorem.


  \begin{freeResponse}
    So let's list and explain the triangle congruence theorems:
    \begin{description}
    \item[\wedn\bfseries\underline{SSS}:] If I know three side lengths
      of a triangle,
      \begin{center}
      \begin{tikzpicture}[geometryDiagrams]
        \coordinate (A) at (0,0);
        \coordinate (B) at (2,2);
        \coordinate (C) at (7,0);
        \tkzDrawSegment (A,B)
        \tkzDrawSegment (A,C)
        \tkzDrawSegment (C,B)
        \tkzLabelSegment[above left](A,B){$c$}
        \tkzLabelSegment[below](A,C){$b$}
        \tkzLabelSegment[above right](B,C){$a$}  

        \tkzMarkAngle[size=0.8cm,thin,mark=](C,A,B)
        \tkzLabelAngle[pos=.6](C,A,B){$?$}

        \tkzMarkAngle[size=0.8cm,thin,mark=](A,B,C)
        \tkzLabelAngle[pos=.5](A,B,C){$?$}

        \tkzMarkAngle[mark=,size=1.5,thin](B,C,A)
        \tkzLabelAngle[pos=1.2](B,C,A){$?$}
        
      \end{tikzpicture}
      \end{center}
      then I can find all the angles of the triangle.
    \item[\wedn\bfseries\underline{SAS}:] If I know two sides lengths
      of a triangle and I know the angle between these two sides,
      \begin{center}
      \begin{tikzpicture}[geometryDiagrams]
        \coordinate (A) at (0,0);
        \coordinate (B) at (2,2);
        \coordinate (C) at (7,0);
        \tkzDrawSegment (A,B)
        \tkzDrawSegment (A,C)
        \tkzDrawSegment (C,B)
        \tkzLabelSegment[above left](A,B){$c$}
        \tkzLabelSegment[below](A,C){$b$}
        \tkzLabelSegment[above right](B,C){$?$}  

        \tkzMarkAngle[size=0.8cm,thin,mark=](C,A,B)
        \tkzLabelAngle[pos=.6](C,A,B){$\alpha$}

        \tkzMarkAngle[size=0.8cm,thin,mark=](A,B,C)
        \tkzLabelAngle[pos=.5](A,B,C){$?$}

        \tkzMarkAngle[mark=,size=1.5,thin](B,C,A)
        \tkzLabelAngle[pos=1.2](B,C,A){$?$}
        
      \end{tikzpicture}
      \end{center}
      then I can find the third side of the triangle, and the other
      two angles.
    \item[\wedn\bfseries\underline{ASA}:] If I know two angles of a
      triangle and the length of the side between these two angles,
      \begin{center}
        \begin{tikzpicture}[geometryDiagrams]
        \coordinate (A) at (0,0);
        \coordinate (B) at (2,2);
        \coordinate (C) at (7,0);
        \tkzDrawSegment (A,B)
        \tkzDrawSegment (A,C)
        \tkzDrawSegment (C,B)
        \tkzLabelSegment[above left](A,B){$?$}
        \tkzLabelSegment[below](A,C){$b$}
        \tkzLabelSegment[above right](B,C){$?$}  

        \tkzMarkAngle[size=0.8cm,thin,mark=](C,A,B)
        \tkzLabelAngle[pos=.6](C,A,B){$\alpha$}

        \tkzMarkAngle[size=0.8cm,thin,mark=](A,B,C)
        \tkzLabelAngle[pos=.5](A,B,C){$?$}

        \tkzMarkAngle[mark=,size=1.5,thin](B,C,A)
        \tkzLabelAngle[pos=1.2](B,C,A){$\gamma$}
        
      \end{tikzpicture}
      \end{center}
      then I can find the other two sides of the triangle, and the
      third angle.
    \item[\wedn\bfseries\underline{AAS}:] If I know two angles of a
      triangle along with a side not between the two angles,
      \begin{center}
        \begin{tikzpicture}[geometryDiagrams]
        \coordinate (A) at (0,0);
        \coordinate (B) at (2,2);
        \coordinate (C) at (7,0);
        \tkzDrawSegment (A,B)
        \tkzDrawSegment (A,C)
        \tkzDrawSegment (C,B)
        \tkzLabelSegment[above left](A,B){$?$}
        \tkzLabelSegment[below](A,C){$?$}
        \tkzLabelSegment[above right](B,C){$a$}  

        \tkzMarkAngle[size=0.8cm,thin,mark=](C,A,B)
        \tkzLabelAngle[pos=.6](C,A,B){$\alpha$}

        \tkzMarkAngle[size=0.8cm,thin,mark=](A,B,C)
        \tkzLabelAngle[pos=.5](A,B,C){$?$}

        \tkzMarkAngle[mark=,size=1.5,thin](B,C,A)
        \tkzLabelAngle[pos=1.2](B,C,A){$\gamma$}
        
      \end{tikzpicture}
      \end{center} the I can find the other two sides, and the third angle.
    \end{description}



    Finally, I claim that there is no SSA congruence theorem. Behold:

    \begin{center}
      GIVE AN EXAMPLE!
    \end{center}
    
  \end{freeResponse}
\end{question}


\begin{question}
  Use one of the congruence theorems to explain WHY the ``triangle is
  the strongest shape.''  In particular, explain why a
  quadrilateral does not make a ``strong shape.''
  \begin{freeResponse}
    We say a triangle is a strong shape because SSS

    Quadrilateral would be floopy.
  \end{freeResponse}
\end{question}



\end{document}
