\documentclass[handout,nooutcomes,noauthor,hints]{ximera}

\input{../preamble.tex}
\title{Rep-tiles}

\author{Bart Snapp}

\begin{document}
\begin{abstract}
  We will investigate rep-tiles.
\end{abstract}
\maketitle



\begin{listOutcomes}
\item Explain what a rep-tile is.
\item Give basic examples of rep-n-tiles.
\end{listOutcomes}


A \textbf{rep-tile}\index{rep-tile} is a polygon where several copies
of a given rep-tile fit together to make a larger, similar (MEANING
SCALED), version of itself. If $2$ copies are used, we call it a
\textit{rep-2-tile}, if $3$ copies are used, we call it a
\textit{rep-3-tile}, and if $n$ copies are used, we call it a
\textit{rep-n-tile}.

\mynewpage

\begin{question}
EXPLAIN why using words, pictures, computations, and so on, as
needed/helpful:
\begin{enumerate}
\item An isosceles right triangle whose sides have lengths $1''$,
  $1''$, and $\sqrt{2}''$ is a rep-2-tile.
\item A rectangle whose sides have lengths $1''$ and $\sqrt{2}''$ is a
  rep-2-tile.
\item Geometry Giorgio suggests that a rectangle whose sides have
  lengths $1''$ and $4''$ is also a rep-2-tile. Is he correct?
  \item Search the internet for other examples of rep-2-tiles, you
    might find a surprise. DISPLAY one of the other rep-2-tiles below.
    \begin{hint}
      You might want to include the word ``dragon'' in your
      search.
    \end{hint}
\end{enumerate}
\begin{freeResponse}
  \begin{enumerate}
  \item Behold:
  \item Behold:
  \item NO WAY!
  \item Here is a DRAGON rep-2-tile.
  \end{enumerate}
\end{freeResponse}
\end{question}
\mynewpage


\begin{question}
EXPLAIN why using words, pictures, and so on, as needed/helpful:
\begin{enumerate}
\item A rectangle whose sides have lengths $1''$ and $\sqrt{3}''$, is a rep-3-tile.
\item A 30-60-90 right triangle whose shortest side has length $1''$, is a rep-3-tile.
\end{enumerate}
\begin{freeResponse}
  \begin{enumerate}
  \item Behold:
  \item Behold:
  \end{enumerate}
\end{freeResponse}
\end{question}
\mynewpage



\begin{question}
EXPLAIN why EVERY triangle and EVERY parallelogram is a rep-4-tile.
DISPLAY a representative example of each.
\begin{freeResponse}
  \begin{enumerate}
  \item Behold:
  \item Behold:
  \end{enumerate}
\end{freeResponse}
\end{question}

\end{document}
