\documentclass[handout,nooutcomes,noauthor,hints]{../ximera}

\input{../preamble.tex}

\title{Measuring Stairs}

\author{Claire Merriman}

\begin{document}
\begin{abstract}
  Let's go outside and measure some staircases.
\end{abstract}
\maketitle


\begin{listOutcomes}
\item Apply formulas to compute the length and width of a staircase.
\item Determine the maximum number of stairs that can fit in a given area.
\end{listOutcomes}

\begin{listObjectives}
\item Determine a reasonable estimate before preforming a calculation,

\item Learn and apply basic geometric formulas.

\end{listObjectives}


\begin{question}
 According to this  \emph{ArchDaily} article, \footnote{https://www.archdaily.com/892647/how-to-make-calculations-for-staircase-designs}  the ideal tread length with for a staircase with $18\ cm$ risers is $27-29\ cm$.
 
 \begin{center}
  \begin{tikzpicture}[scale = .3]
    \draw[thick]
    (10,0) -- (9,0) -- (9,1) -- (8,1) --
    ( 8,2) -- (7,2) -- (7,3) -- (6,3) --
    ( 6,4) -- (5,4) -- (5,5) -- (4,5) --
    ( 4,6) -- (3,6) -- (3,7) -- (2,7) --
    ( 2,8) -- (1,8) -- (1,9) -- (0,9) --
    (0,10) -- (0,0) -- (10,0);
    \draw [decorate,decoration={brace,amplitude=10pt,mirror},xshift=-4pt,yshift=0pt,]
    (0,10) -- (0,0) node [black,midway,xshift=-1cm] 
          {\footnotesize $10\ stairs$};
    \draw [decorate,decoration={brace,amplitude=10pt},xshift=0pt,yshift=-4pt,]
    (10,0) -- (0,0) node [black,midway,yshift=-.8cm] 
          {\footnotesize $10\ stairs$};     
\end{tikzpicture}
\end{center}

You are trying to determine how much space you need for a staircase that is $180\ cm$ tall.  

\begin{itemize}
 \item[\emph{Think:}] What is the minimum length of the staircase, using $18\ cm$ risers and the ideal tread length? What is the maximum?
 \item[\emph{Pair:}] Why?
 \item[\emph{Share:}] How do your answers change after the group discussion?
\end{itemize}
\end{question}

\mynewpage

\begin{question}
 You want to build a staircase that is $310\ cm$ (roughly $10'$) tall. Considering an ideal riser of $18\ cm$, the height of the space is divided by the height of each step. The result should always be rounded up.
 
\begin{enumerate}
 \item How many stairs would you need? Why?
 \item How tall are the risers? Why?
 \item Using the same ideal tread length of $27-29\ cm$,  what is the minimum length of the staircase? What is the maximum? Why?
\end{enumerate}
\end{question}

\mynewpage

\begin{question}
 Now we are going to gather some real world data. In you groups, you will find a staircase near the classroom to measure. We will start by doing an example staircase as a class.
 
Make sure to return to class by $1:25pm$, so that we have enough time to go over the data as a class.
 
 \textbf{Upload a photos of your group measuring the staircase. The ruler should be legible for both height and width.} You may either include the photo in homework file, or submit it as a group to the ``Photo For September 20" assignment. 
 
 \resizebox{\textwidth}{!}{%
 {\renewcommand{\arraystretch}{4}
\begin{tabular}{|r|r|r|r|r|r|r|r|r|}\hline
 &Example&Group 1& Group 2& Group 3& Group 4 & Group 5& Group 6& Group 7\\\hline
 Riser Height & &&&&&&&\\\hline
 Tread width & &&&&&&&\\\hline
Number of Stairs& &&&&&&&\\\hline
 Staircase Height & &&&&&&&\\\hline
Staircase Width& &&&&&&&\\\hline
\end{tabular}
}
}
\end{question}
\end{document}