\documentclass[noauthor,nooutcomes]{ximera}

\input{../preamble}

\author{Claire Merriman and Bart Snapp}

\checkYourselfAbstract

\begin{document}
\maketitle

\begin{exercise}
  True or False:
 The sum of the exterior angles of any polygon on a flat surface is $360^\circ$.
\end{exercise}

\begin{exercise}
  True or False: If you walk Louie Llama around an $n$-gon, he will
  rotate $n\cdot 180$ degrees.
\end{exercise}




\begin{exercise}
 Consider the following equation: $(80-\alpha)+(80-\beta)+(80-\gamma)=40$. Solve for $\alpha+\beta+\gamma$.
\end{exercise}



\begin{exercise}
 Consider the following equation: $(30-\alpha)+(40-\beta)+(60-\gamma)=10$. Solve for $\alpha+\beta+\gamma$.
\end{exercise}


\begin{exercise}
The \mooculus~Design company wants to hire a mathematical
designer. Knowing that you once took a mathematics class, they ask you
to sit in on the interviews.


You don't remember much--but you do recall that when drawing shapes
one needs to be careful with interior and exterior angles.

 

Which question below would be best to ask if you want to know if the
job candidate knows the difference between interior and exterior
angles?

\begin{enumerate}
\item You ask them about interior/exterior angles of any
  triangle.
\item You ask them about interior/exterior angles of a square.
\item You ask them about interior/exterior angles of a circle.
\item Any shape will work for this sort of question.
\end{enumerate}

\end{exercise}






\answerlistbox{True}{False}{$\alpha+\beta+\gamma=200$}{$\alpha+\beta+\gamma=120$}{(a)}
\end{document}
