\documentclass[noauthor,nooutcomes,12pt]{ximera}

\input{../../preamble.tex}
\input{../../activityPreamble.tex}


\title{Repeating steps}
\author{Bart Snapp}

\begin{document}
\begin{abstract}
  Don't type so much, let the turtle repeat!
\end{abstract}
\maketitle

\nameblankgen

\begin{multicols}{2}
  Drawing picturs in \LOGO\ often means making the turtle do things
  over and over again. The drawing-turtle doesn't mind, but there are
  efficient ways to communicate. One way is the \lc{repeat} command.
\begin{logo}
repeat 4 [
  fd 100
  lt 90
  ]
\end{logo}

Remember, she's a drawing turtle, drawing a path wherever she goes.

To help her turn, use a command like \lc{lt 90} to mean ``turn $90$
degrees to the left.'' So for example, the code below draws a square:

\begin{logo}
fd 100
lt 90
fd 100
lt 90
fd 100
lt 90
fd 100
\end{logo}
\begin{logoout}
\begin{tikzpicture}[turtle/distance=2cm]
  \draw [thick,black,turtle={home,forward,left,forward,left,forward,left,forward}];
  \node at (0,0) {\turtler};
\end{tikzpicture}
\end{logoout}

Note, now she has turned, and is pointing directly right, like
$\turtler$, thus proving the old adage,
\begin{quote}
  Two wrongs don't make a right, but four lefts do.
\end{quote}
\end{multicols}

\newpage

\begin{problem}
  Use the techniques above to help the turtle draw an equilateral
  triangle with side length $250$. Show your code and your picture.
\end{problem}

\newpage

\begin{problem}
  Use the techniques above to help the turtle draw a regular pentagon
  triangle with side length $90$. Show your code and your picture. 
\end{problem}

\newpage


\begin{problem}
  Use the techniques above to help the turtle draw an regular hexagon
  with side length $80$. Show your code and your picture. 
\end{problem}

\newpage

\begin{problem}
  Use the techniques above to help the turtle draw a regular
  five-pointed star of a reasonable size. Show your code and your
  picture.
\end{problem}

\newpage

\begin{problem}
  Use the techniques above to draw the rep-4-tile known as the sphinx,
  that is, produce this picture:
  \begin{logoout}
\begin{tikzpicture}[turtle/distance=2cm]
  \draw [thick,black,turtle={home,right,forward,forward,forward,left=120,forward,left=60,forward,right=60,forward,left=120,forward,forward}];
  %\node at (0,0) {\rotatebox{140}{\turtle}};
\end{tikzpicture}
\end{logoout}

  Show your code and your
  picture.
\end{problem}



\end{document}
