\documentclass[handout,nooutcomes,noauthor]{ximera}

\input{../../preamble.tex}
\input{../../activityPreamble.tex}

\title{Star maker}

\author{Bart Snapp}

\begin{document}
\begin{abstract}
  We will investiagte stars.
\end{abstract}
\maketitle

\noindent\textbf{Group members (please print):}\ \hrulefill \\

\hrulefill

\begin{problem}
  Explain what is meant by the symbol $\star{n}{s}$.
\end{problem}

\begin{problem}
  Use a compass and protractor to draw $\star{6}{s}$ for $s =
  1,2,3,4,5$. Which of these look the same? How many pieces are there in
  each case?
\end{problem}


\begin{problem} Use a compass and protractor to draw $\star{7}{s}$ for $s =
  1,\dots,6$. Which of these look the same? How many pieces are there
  in each case?
\end{problem}

\begin{problem} Use a compass and protractor to draw $\star{8}{s}$ for $s =
  1,\dots,7$. Which of these look the same? How many pieces are there
  in each case?
\end{problem}


\begin{problem}
  Give three different stars each made of 3 connected pieces. Explain
  your reasoning.
\end{problem}


\begin{problem}
  Give a precise description of what happens when we ``reduce to
  lowest terms.'' As an example, think about how the stars
  $\star{6}{2}$ and $\star{3}{1}$ are related. Explain why your
  description holds.
\end{problem}



\begin{problem}
  Draw $\star{4}{2}$, $\star{6}{3}$, and $\star{8}{4}$.  What do you
  notice? Let's call these stars \textit{asterisk stars}. Give a
  precise description of when you can draw asterisk stars---and when
  you cannot draw asterisk stars. Explain why your description holds.
\end{problem}

\begin{problem}
  \textit{Interested Isabel} finds $\star{7}{2}$ and $\star{7}{3}$
  interesting. Why?
\end{problem}

\begin{problem}
  \textit{Interested Isabel} finds $\star{10}{2}$ and $\star{10}{4}$
  interesting. Why?
\end{problem}
\end{document}
