\documentclass[nooutcomes,noauthor,hints,handout,12pt]{ximera}

\input{../preamble.tex}
\title{Voting schemes}

\author{Bart Snapp}

\begin{document}
\begin{abstract}
  We investigate three popular voting schemes for when there are three
  or more options.
\end{abstract}
\maketitle

\begin{listOutcomes}
\item Organize and accommodate data.
\item Critically analyze data.
\item Translate classroom mathematics into real world mathematics.
\end{listOutcomes}


The \mooculus~apartment building is holding an `election' among
their $38$ residents to see if they should allow dogs, or cats, or no
pets at all. Of the residents:
\begin{itemize}
\item $16$ residents prefer dogs, better than cats, better than no pets at all.
\item $4$ residents prefer cats, better than dogs, better than no pets at all.
\item $18$ residents prefer no pets at all, better than cats, better
  than dogs.
\end{itemize}



If there are three or more choices, then we have options as to how
exactly we vote. 
\begin{description}
\item[Plurality Voting:] The option with \textbf{the most
  votes wins}.
\item[Borda Count:] Voters enumerate their preferences with points
  $2,1,0$, with $2$ meaning `most preferred' and $0$ meaning `least
  preferred.'  The option with the \textbf{largest total sum of
    points} from this ranked-vote wins.
\item[Instant Run-Off Voting:] Voters list their preferences from
  `most preferred' to `least preferred.' A plurality vote is taken
  among the most preferred. All votes for losers are transferred to
  remaining two options based on the order. This is also known as
  \textbf{Ranked Choice Voting}.
\end{description}







\mynewpage



%% MAybe do all 3 then analyze?
%1) count
%2) analyze
%3) Borda blues?

\begin{question}
  Compute the outcomes of the \mooculus~apartment pet `election'
  using
  \begin{enumerate}
  \item \textbf{Plurality Voting},
  \item \textbf{Borda Count}, and
  \item \textbf{Instant Run-off Voting}.
  \end{enumerate}
  Explain your reasoning and show all work.
  \begin{freeResponse}
    Using \underline{Plurality Voting}, we see that ``no pets'' wins, as that
    option got $18$ votes, compared to the other option's $16$ and
    $4$.


    
    Using \underline{Borda Count}, we have
    \begin{description}
      \item[Dogs:] $16\cdot 2 + 4 = 36$.
      \item[Cats:] $16 +4\cdot 2+18 =42$.
      \item[No Pets:] $18\cdot 2 = 36$.
    \end{description}
  
  We see that ``cats'' wins.

  

  Using \underline{Instant Run-Off Voting}, we have that ``dogs'' and
  ``no pets'' win the first round, but the $4$ votes for ``cats'' go
  to ``dogs'' next, and ``dogs'' win.
  \end{freeResponse}
\end{question}
\mynewpage



\begin{question}
  Analyze the results of each of your `elections' from above. \textbf{For each
  method of counting the vote,} answer
  \begin{enumerate}
  \item How many people got their most preferred option?
  \item How many people got their medium option? 
  \item How many people got their least preferred option?
  \end{enumerate}
  by filling in the table below:
  \begin{center}\renewcommand{\arraystretch}{1.5}
    \begin{tabular}{|l||c|c|c|}\hline
      Voting Scheme & \# most preferred & \# medium & \# least preferred \\ \hline\hline
      Plurality  Voting &  \rule[7mm]{10mm}{0mm}& & \\ \hline
      Borda Count &  \rule[7mm]{10mm}{0mm}&  & \\ \hline
      Instant Run-Off Voting & \rule[7mm]{10mm}{0mm}&  &\\\hline
    \end{tabular}
  \end{center}
  
  After you have evaluated each voting system, which \textbf{voting system} do
  \textbf{you think} the tenants of the apartment should use? Explain why you make this choice. 
\end{question}
\mynewpage








\begin{question}
  Find a \textbf{real-world example of Instant Run-Off Voting} (Rank Choice Voting) and a
  \textbf{real-world example of Borda Count} being used. Briefly
  describe each situation below.
    
\end{question}

\end{document}
