\documentclass[nooutcomes,noauthor]{ximera}

\input{../preamble}

\author{Bart Snapp}

\checkYourselfAbstract

\begin{document}
\maketitle



\begin{exercise}
  FedEx revolutionized the shipping business by:
    \begin{enumerate}
    \item Having a warehouse equidistant from common delivery cities.
    \item Using trucks that are mounted on the chassis of cars, so they
      can drive through cities easily.
    \item Using electric vehicles to save on fuel.
    \item Using computers to track shipments.
    \end{enumerate}
\end{exercise}





\begin{exercise}
  Suppose you have two nails in the wall. Now you take a loop of
  string, and make a triangle with a pencil, the string and the two
  nails. If you keep the string taught, what can you draw with your
  pencil?
    \begin{enumerate}
\begin{multicols}{2}
 \item A line.
 \item A circle. 
 \item A triangle.
 \item An ellipse.
\end{multicols}
\end{enumerate}
\end{exercise}

\begin{exercise}
  If you want to find the circumcenter of a triangle, you should:
  \begin{enumerate}
  \item Intersect the angle bisectors.
  \item Intersect the perpendicular bisectors of the sides.
  \item Connect the midpoint of the sides to the opposite angles.
  \end{enumerate}
\end{exercise}


\begin{exercise}
  True or False: The circumcenter of a triangle is always inside the
  triangle.
\end{exercise}


\begin{exercise}True or False:
  Suppose I have a $2$-dimensional shape that looks like it might be a
  circle. If I measure the diameters and they are all the same length, then
  it must be a circle.
\end{exercise}

\answerlistbox{(a)}{(d)}{(b)}{False}{False}
\end{document}
