\documentclass[nooutcomes,noauthor,handout,hints,12pt]{ximera}

\input{../preamble.tex}
\title{Volume of pyramids}

\author{Jenny Sheldon \and Bart Snapp}

\begin{document}
\begin{abstract}
  We build a formula for the volume of a pyramid based on the volume
  of a box.
\end{abstract}
\maketitle


\begin{listOutcomes}
\item Dissect a cube into three right pyramids.
\item Find the volume of right pyramid.
\item State Cavalieri's shearing principle in three dimensions.
\item Apply Cavalieri's shearing principle to derive the volume of ANY pyramid
  of height $s$ over an $s\times s$ square base.
\item Explain how shapes of the same volume can have drastically
  different surface areas.
\item Apply the distributive property in a geometric setting.
\end{listOutcomes}

%% \begin{listObjectives}
%%  \item Explain why presented concepts and formulas are true,
%%  \item Take a solution to a problem in a given context, and applying that same solution to another problem,
%%  \item Increase student confidence in their ability to solve difficult math problems by using previous results, trying different methods, asking questions, and working with others,
%%  \item Improve student’s mathematical communication skills.

%% \end{listObjectives}

\mynewpage


\begin{question}
  Give detailed diagrams with explanation showing that a cube can be
  constructed from three identical square-based pyramids.
  \begin{freeResponse}
    Here they are:
    \begin{center}
    \begin{tikzpicture}
      \coordinate (A) at (0,0,0);
      \coordinate (B) at (4,0,0);
      \coordinate (C) at (4,4,0);
      \coordinate (D) at (0,4,0);
      \coordinate (A') at (0,0,4);
      \coordinate (B') at (4,0,4);
      \coordinate (C') at (4,4,4);
      \coordinate (D') at (0,4,4);
      
      
      
      %\draw[fill=red,opacity=0.3] (A)--(B)--(C)--(D)--cycle; % base
      %\draw[fill=blue,opacity=0.3] (A')--(B')--(C')--(D')--cycle; % base
      %% \draw[fill=orange,opacity=0.3] (B1)--(B2)--(peak);
      %% \draw[fill=yellow,opacity=0.3] (B2)--(B3)--(peak);
      %% \draw[fill=green,opacity=0.3] (B3)--(B4)--(peak);
      %% \draw[fill=blue,opacity=0.3] (B4)--(B5)--(peak);
      %% \draw[fill=purple,opacity=0.3] (B5)--(B1)--(peak);

      
      \draw (A)--(B)--(C)--(D)--cycle;
      \draw (A)--(A');
      \draw (B)--(B');
      \draw (C)--(C');
      \draw (D)--(D');
      \draw (A')--(B')--(C')--(D')--cycle;
      
      \draw[line width=3.5pt,red] (A)--(A');
      \draw[line width=3.5pt,red] (A')--(B');
      \draw[line width=3.5pt,red] (B)--(B');
      \draw[line width=3.5pt,red] (B)--(A);
      \draw[line width=3.5pt,red] (A')--(D);
      \draw[line width=3.5pt,red] (B)--(D);
      \draw[line width=3.5pt, red] (B')--(D);
      \draw[line width=3.5pt, red] (A)--(D);

      \draw[line width=2pt,blue] (C')--(C);
      \draw[line width=2pt,blue] (C')--(D);
      \draw[line width=2pt,blue] (C)--(D);
      \draw[line width=2pt,blue] (B)--(D);
      \draw[line width=2pt,blue] (B')--(D); %% diagonal
      \draw[line width=2pt,blue] (B')--(B);
      \draw[line width=2pt, blue] (B')--(C');
      \draw[line width=2pt, blue] (B)--(C);

      
    \end{tikzpicture}
  \end{center}
\end{freeResponse}
\end{question}
\mynewpage


\begin{question}
  Let us work analogously to what we did in the triangle case.
  
  \begin{enumerate}
  \item Use your work above to derive a formula for the volume of a
    right square-based pyramid whose height is $s$ with an $s\times s$
    square base. Explain your reasoning.
  \item State Cavalieri's principle in three dimensions. Explain what Cavalieri's principle means using words, pictures etc.
  \item Give a formula for the volume of \emph{any} (not necessarily
    ``right'') pyramid of height $s$ over an $s\times s$ square
    base. Explain your reasoning.
  % \item Explain how to use a picture to prove that a pyramid of a
  %   given (fixed) volume could have an arbitrarily large surface area.
  \item What if the base of the pyramid is $s\times s$ but the height is $h$? What's the volume now?
  \end{enumerate}
  \begin{freeResponse}
    \begin{enumerate}
    \item The volume of a cube is $s^3$. Since $3$ right pyramids make up
    this cube, a right pyramid of side length $s$ and height $s$ must
    have a volume of:
    \[
    \frac{s^3}{3}
    \]
    \item Here we break up the $a\times b\times h$ box into 
    \end{enumerate}
\end{freeResponse}
\end{question}
\mynewpage

\begin{question}
  Let's extend these ideas further:
  \begin{enumerate}
  \item Now consider a pyramid of height $h$ with an $1\times 2$
    rectangular base. Use your work above (and the distributive
    property) to derive a formula for the volume of this
    pyramid in terms of the area of the rectangle. Explain your reasoning with words, pictures and such.
    \item Now consider a pyramid of height $h$ with an $2\times 6$
    rectangular base. Use your work above (and the distributive
    property) to derive a formula for the volume of this
    pyramid in terms of the area of the reactangle. Explain your reasoning with words, pictures and such.
  \item Finally, consider a cone of height $h$ over a blobby shape of
    area $A$. Use your previous work to derive a formula for the
    volume of this solid in terms of the area $A$ and the height. Explain your reasoning with words, pictures and such.
    \begin{hint}
      Start by chopping the blobby shape into little squares. Then use your previous ideas.
    \end{hint}
  \end{enumerate}
    \begin{freeResponse}
Not written yet
    \end{freeResponse}
\end{question}


\end{document}
