\documentclass[nooutcomes,noauthor]{ximera}

\input{../preamble}

\author{Bart Snapp}

\checkYourselfAbstract

\begin{document}
\maketitle



\begin{exercise}
  Here are some facts:
  \begin{itemize}
      \item Hospital patients who are transported via helicopter
        after a serious accident have a higher probability of
        surviving than those who travel an in ambulance.
      \item Hospital patients who are transported via helicopter
        after a nonserious accident have a higher probability of
        surviving than those who travel an in ambulance.
      \item Overall, hospital patients who are transported in an
        ambulance have a higher chance of surviving than those who travel in a helicopter.
  \end{itemize}
        
  
  True or False: This is an example of Simpson's paradox.
 
\end{exercise}




\begin{exercise}
  It's a fact: \link[Roads cause
    traffic]{https://en.wikipedia.org/wiki/Braess's_paradox}. Moreover,
  removing roads can actually reduce traffic congestion.

  
  True or False: This is an example of Simpson's paradox.

\end{exercise}

\begin{exercise}
  You and your friend decided to have a free-throw contest.
  \begin{itemize}
  \item On Day 1, you make $80$ attempts and succeed at $70\%$. Your friend makes $40$ attempts and succeeds at $71\%$.
  \item On Day 2, you make $20$ attempts and succeed at $60\%$. Your friend makes $60$ attempts and succeeds at $61\%$.
  \end{itemize}
  Who won your free-throw contest?
  \begin{enumerate}
  \item You
  \item Your friend
  \item Impossible to say
  \end{enumerate}

\end{exercise}



\begin{exercise}
  It is possible for the majority of voters to prefer a candidate,
  where districting causes this candidate to loose.

  
  True or False: This is an example of Simpson's paradox.

\end{exercise}




\begin{exercise}
  True or False:
  
  If you encounter Simpson's paradox, it's an indication that you have
  made a mistake collecting data.
 
\end{exercise}



\answerlistbox{True}{False}{(a)}{True}{False}
\end{document}
