\documentclass[nooutcomes,noauthor,hints,handout]{ximera}

\input{../preamble.tex}
\title{Simpsons paradox}


%% https://en.wikipedia.org/wiki/Simpson%27s_paradox
%% https://www.amazon.com/Mathematician-Ballpark-Odds-Probabilities-Baseball/dp/0452287820
%% https://aperiodical.com/2013/01/as-maths-results-and-batting-averages/gyz
% https://pubmed.ncbi.nlm.nih.gov/16931545/


%%% https://stats.stackexchange.com/questions/518146/how-to-handle-simpsons-paradox%% \[


\author{Bart Snapp}

\begin{document}
\begin{abstract}
  Let's examine some confusing data.
\end{abstract}
\maketitle

\begin{listOutcomes}
\item Work with real-world numbers.
\item Critically analyze data.
\item Explain patterns in data from a mathematical point of view.
\item Explain patterns in data from a qualitative point of view.
\end{listOutcomes}


A \textbf{paradox} in mathematics is something that \textit{seems
contradictory} but isn't.



\textbf{Simpson's paradox} occurs when a data set seems to
simultaneously \textit{support and refute} a hypothesis, based on how
the data is organized.



Let's investigate some examples of Simpson's paradox. 


\mynewpage



\begin{question}

  \link[Studies on mortality and tobacco
    use]{https://www.valueinhealthjournal.com/article/S1098-3015(15)02902-2/fulltext}
  show that at each age, smokers are more likely to die of
  cardiovascular disease than nonsmokers.  However, when examining
  deaths due to cardiovascular disease at all ages together, smokers
  are less likely to die of cardiovascular disease than nonsmokers.

\begin{enumerate}
\item This is an example of Simpson's paradox. What's the paradox?
\item How can we reconcile this data?
\item Who is more likely to die of cardiovascular disease, smokers or
  nonsmokers?
\item Does not smoking ensure you won't die of cardiovascular disease?
\end{enumerate}
\end{question}
\mynewpage




\begin{question}
In Ken Ross's book \textit{A Mathematician at the Ballpark: Odds and Probabilities for Baseball Fans}, he points out the following about batting averages:
\[
\begin{array}{|c||c|c|c|} \hline
 & 1995~\text{Batting Avg.} & 1996~\text{Batting Avg.}& \text{Combined}\\ \hline\hline
\text{Derek Jeter} & 12/48 = 0.250 & 183/582 = 0.314 & 195/630 =0.310\\ \hline
\text{David Justice} & 104/411=0.253 & 45/140=0.321  & 149/551 = 0.270\\ \hline
\end{array}
\]
\begin{enumerate}
\item This is an example of Simpson's paradox. What's the paradox?
\item How can we reconcile this data?
\item Who was the better batter, Jeter or Justice?
\item Does being the best each year ensure you'll be best overall?
\end{enumerate}
\end{question}
\mynewpage








\begin{question}
In the 1970's a scandal arose at the University of California,
Berkeley. There was a distinct gender bias against women in the number
of graduate students admitted among the 6 largest departments:
\begin{center}
\begin{tabular}{|c||c|c|} \hline
 & Applicants & Admitted \\ \hline\hline
Men & 2590 & 46\% \\ \hline
Women & 1835 & 30\% \\ \hline
\end{tabular}
\end{center}
Data from individual departments was collected for further investigation:
\[
\begin{array}{|c||c|c||c|c|} \hline
\multirow{2}{*}{\text{Department}} & \multicolumn{2}{c||}{\text{Men}} & \multicolumn{2}{c|}{\text{Women}}  \\\cline{2-5}
 & \text{Applicants} & \text{Admitted} & \text{Applicants} & \text{Admitted} \\\hline\hline
A & 825 & 62\% & 108 & 82\%\\ \hline
B & 560 & 63\% & 25 & 68\% \\ \hline
C & 325 & 37\% & 593 & 34\% \\ \hline
D & 417 & 33\% & 375 & 35\% \\ \hline
E & 191 & 28\% & 393 & 24\% \\ \hline
F & 272 & 6\% & 341 & 7\% \\ \hline
\end{array}
\]

\begin{enumerate}
\item This is an example of Simpson's paradox. What's the paradox?
\item How can we reconcile this data?
\item Did Berkeley sexually discriminate? If not where did the discrimination come from?
\item Does not discriminating in every department ensure there is not discrimination?
\end{enumerate}

\end{question}



\end{document}
