\documentclass[handout,noauthor,nooutcomes,hints]{ximera}
\input{../preamble.tex}
\title{Getting started}
\author{Claire Merriman and Bart Snapp}

\begin{document}
\begin{abstract}
  We make estimates of every-day objects in every-day settings and we
  observe the effects of scaling when we change objects.
\end{abstract}
\maketitle


%% \begin{listObjectives}
%%  \item{Determine a reasonable estimate before preforming a calculation.}
%%  \item{Increase student confidence in their ability to solve difficult math problems by using previous results, trying different methods, asking questions, and work- ing with others.}
%% \end{listObjectives}

\begin{listOutcomes}
\item{Edit/create PDFs to create completed journal entries.}
\item{Hand-in journal entries online.}
\item{Work in nonstandard units.}
\item{Estimate areas and volumes in nonstandard units.}
\item{Critique and dismantle reasonable hypotheses in regard to geometry and arithmetic.}
\end{listOutcomes}

\mynewpage


\begin{question}
Look around our classroom. How many tennis balls would it take to
\begin{enumerate}
\item Line one edge of the classroom?
 \item Cover the floor?
 \item Fill the room?
\end{enumerate}
In each case, EXPLAIN how you arrive at your conclusion.
\end{question}
\mynewpage





\begin{question}
Look around our classroom. How many ping pong balls would it take to
\begin{enumerate}
\item Line one edge of the classroom?
\item Cover the floor?
\item Fill the room?
\end{enumerate}
In each case,  EXPLAIN how you arrive at your conclusion.
\end{question}
\mynewpage




\begin{question}
  You notice that a tennis ball has about twice the diameter of a ping
  pong ball. When you mention this to your friend and fellow student
  \textit{Geometry Giorgio}, he suggests that we think in the
  following way:
\begin{quote}
  Since a tennis ball has about twice the diameter of a ping pong
  ball, the answers for Problem $2$ above should all be about twice the
  answers from Problem $1$.
\end{quote}
Is \textit{Geometry Giorgio} correct?  If he is correct, explain
why. If he is not correct, try to salvage and correct his reasoning.
\end{question}



\end{document}
