\documentclass[noauthor]{ximera}

\input{../preamble}

\author{Bart Snapp}

\checkYourselfAbstract

\begin{document}
\maketitle


\begin{exercise}
If you fold a sheet of paper in half, its thickness doubles. A standard sheet is $0.1$ mm thick.
Folding in half each time, after  $10$ folds, how thick is it?
\begin{enumerate}
  \item about $1$ cm
  \item about $10$ cm
  \item about $100$ cm
  \item about $1000$ cm
\end{enumerate}
\end{exercise}

\begin{exercise}
  A single lily pad on a pond doubles in number every day. After 20 days, the pond is fully covered.
  On what day was the pond half covered?
\end{exercise}


\begin{exercise}
  A single lily pad on a pond doubles in number every day. After 20 days, the pond is fully covered.
  On what day was it only $1/16$ covered?
\end{exercise}


\begin{exercise}
  A king offers a servant one grain of rice on the first square of a chessboard and doubles it on each of the 64 squares.
  How many grains are on the 64th square?
  \begin{enumerate}
    \item Around $10^{19}$
    \item Around $10^{20}$ 
    \item Around $10^{21}$ 
  \end{enumerate}
\end{exercise}


\begin{exercise}
Which of the following situations best represents exponential growth?
\begin{enumerate}
\item A factory produces $50$ bicycles every day, increasing total production by the same amount each day.
\item A tree grows $3$ inches taller every year, regardless of its current height.
\item A rumor spreads so that each person who hears it tells two new people every day.
\item A parking lot adds $10$ new parking spaces each month.
\end{enumerate}
\end{exercise}

\answerlistbox{(b)}{$19$}{$16$}{(a)}{(c)}
\end{document}
