%\documentclass[handout]{ximera}
\documentclass[nooutcomes,noauthor]{ximera}

\input{../../preamble}
\input{../../activityPreamble.tex}

\title{More transformations}
\author{Bart Snapp and Brad Findell}

\outcome{Learning outcome goes here.}

\begin{document}
\begin{abstract}
  We think about geometric transformations.
\end{abstract}
\maketitle

\noindent\textbf{Group members (please print):}\ \hrulefill \\

\hrulefill

%% \begin{teachingnote}
%% Supplies:  tracing paper.  Helpful to label the vertices and pay attention to where they go in the symmetry transformation.  The named lines of symmetry don't move when the figure moves.
%% \end{teachingnote}

Transformations of the plane are considered to be functions that take points as inputs and produce 
points as outputs.  Given a point as input, the corresponding output value is often called 
the \emph{image} of the point under the transformation.%% \margincomment{CCSS G-CO.2. Represent transformations in the plane using, e.g.,
  %% transparencies and geometry software; describe transformations as
  %% functions that take points in the plane as inputs and give other
  %% points as outputs. Compare transformations that preserve distance
  %% and angle to those that do not (e.g., translation versus horizontal stretch).}
\begin{problem}
Based on your experience with the basic rigid motions, write definitions of translation, rotation, and reflection.%% \margincomment{CCSS G-CO.4. Develop definitions of rotations, reflections, and translations 
  %% in terms of angles, circles, perpendicular lines, parallel lines,
%and line segments.}
  For each definition, be sure to indicate what it
  takes to specify the transformation.
\begin{enumerate}
\item Translation: 
\vspace{0.3in}
\item Rotation: 
\vspace{0.3in}
\item Reflection: 
\vspace{0.3in}
\end{enumerate}
\end{problem}

\begin{problem}
Describe briefly what you can say about each of the following
sequences of basic rigid motions.  Include examples in your
descriptions.
\begin{enumerate}
\item Translation followed by translation
\vspace{0.5in}
\item Rotation followed by rotation
\vspace{0.5in}
\item Reflection followed by reflection
\vspace{0.5in}
\item Translation followed by rotation
\vspace{0.5in}
\item Translation followed by reflection
\vspace{0.5in}
\item Rotation followed by reflection
\end{enumerate}
\end{problem}
\end{document}
