\documentclass[nooutcomes,noauthor]{ximera}

\input{../preamble}

\author{Bart Snapp}

\checkYourselfAbstract

\begin{document}
\maketitle

The \mooculus~Lunch-Time Club is holding an `election' among their
$23$ members for the ``Best Lunch-Time Food.'' Of the members:
\begin{itemize}
\item $7$ members prefer hamburgers, better than pizza, better than tacos. 
\item $10$ members prefer tacos, better than pizza, better than hamburgers. 
\item $6$ members prefer pizza, better than hamburgers, better than tacos.
  than dogs.
\end{itemize}

\begin{exercise}
  True or False: All voting systems give the same winner.
 
\end{exercise}


\begin{exercise}
  Who wins the election above if Plurality Voting is used to count the
  vote?
  \begin{multicols}{3}
  \begin{enumerate}
  \item Hamburgers
  \item Pizza
  \item Tacos
  \end{enumerate}
  \end{multicols}
\end{exercise}



\begin{exercise}
  Who wins the election above if the Borda Count is used to count the
  vote?
  \begin{multicols}{3}
  \begin{enumerate}
  \item Hamburgers
  \item Pizza
  \item Tacos
  \end{enumerate}
  \end{multicols}
\end{exercise}



\begin{exercise}
  Who wins the election above if Instant Run-Off Voting is used to
  count the vote?
  \begin{multicols}{3}
  \begin{enumerate}
  \item Hamburgers
  \item Pizza
  \item Tacos
  \end{enumerate}
  \end{multicols}
\end{exercise}



\begin{exercise}
  True or False: Borda Count is never used in real-life.
\end{exercise}



\begin{exercise}
  True or False: Instant Run-Off Voting is the same as Ranked Choice Voting.
\end{exercise}


\answerlistbox{(c)}{(b)}{(a)}{False}{True}
\end{document}
