\documentclass[nooutcomes,noauthor]{ximera}

\input{../preamble.tex}
\title{The distance formula}

\author{Bart Snapp}

\begin{document}
\begin{abstract}
  Let's think of consequences of the Pythagorean theorem.
\end{abstract}
\maketitle


\begin{listOutcomes}
\item Find various loci of points.
\item State the definition of a circle.
\item State the definition of an ellipse.
\item{Critique and dismantle reasonable hypotheses in regard to geometry and arithmetic.}
\item State the definition of the circumcenter of a triangle.
\item State the definition of the circumcircle of a triangle.
\item Recognize that circles are determined by three points.
\end{listOutcomes}


\mynewpage



\begin{question}
  Use the INTERNET to look up the distance formula. 
  \begin{enumerate}
    \item STATE the distance formula. 
    \item EXPLAIN (perhaps with the help of a picture) how the
      distance formula follows from the Pythagorean theorem.
    \item A \textbf{circle} is the set of points equidistant from a
      given point. DERIVE (you may use the INTERNET to help you) the
      \textbf{standard equation of a circle} of radius $r$ centered at
      the origin.  
  \end{enumerate}
  \begin{freeResponse}
    \begin{enumerate}
    \item The \underline{distance formula} says that the distance between two points $(x,y)$ and $(a,b)$ is
      \[
      \text{distance} = \sqrt{(x-a)^2 + (y-b)^2}.
      \]
    \item This is basically the Pythagorean theorem. Plot the points
      $(a,b)$ and $(x,y)$:
    \begin{center}
      \begin{tikzpicture}[geometryDiagrams]
	\begin{axis}[
            xmin=0, xmax=5,ymin=0,ymax=5,
            axis lines =left, 
            every axis y label/.style={at=(current axis.above origin),anchor=south},
            every axis x label/.style={at=(current axis.right of origin),anchor=west},
            xtick={1,3}, xticklabels={$a$,$x$},
            ytick={2,3}, yticklabels={$b$,$y$},
            axis on top,
          ]       
          \addplot[,dashed] plot coordinates {(1,0) (1,2)};
          \addplot[,dashed] plot coordinates {(0,2) (1,2)};
          \addplot[,dashed] plot coordinates {(3,0) (3,3)};
          \addplot[,dashed] plot coordinates {(0,3) (3,3)};
          \addplot[,only marks,mark=*] coordinates{(1,2)};  %% closed hole          
          \addplot[,only marks,mark=*] coordinates{(3,3)};  %% closed hole          
        \end{axis}
      \end{tikzpicture}
    \end{center}
    We may now construct a right triangle with horizontal side length
    $(x-a)$ and vertical side length
    $(y-b)$ whose hypotenuse is the shortest path
    between the two points:
    \begin{center}
      \begin{tikzpicture}[geometryDiagrams]
        \begin{axis}[
            xmin=0, xmax=5,ymin=0,ymax=5,
            axis lines =left, 
            every axis y label/.style={at=(current axis.above origin),anchor=south},
            every axis x label/.style={at=(current axis.right of origin),anchor=west},
            xtick={1,3}, xticklabels={$a$,$x$},
            ytick={2,3}, yticklabels={$b$,$y$},
            axis on top,
          ]       
          \node at (axis cs:2,1.75) {$(x-a)$}; 
          \node at (axis cs:3.5,2.5) {$(y-b)$}; 
          \addplot[dashed] plot coordinates {(1,2) (3,3)};
          \addplot[] plot coordinates {(1,2) (3,2)};
          \addplot[] plot coordinates {(3,2) (3,3)};
          \addplot[] plot coordinates {(2.83,2) (2.83,2.2) (3,2.2)};
          \addplot[,only marks,mark=*] coordinates{(1,2)};  %% closed hole          
          \addplot[only marks,mark=*] coordinates{(3,3)};  %% closed hole          
        \end{axis}
      \end{tikzpicture}
    \end{center}
    By the Pythagorean theorem, the length of this path is given by 
    \[
    \text{distance}=\sqrt{(x-a)^{2}+(y-b)^{2}}.
    \]
  \item Well, write
      \begin{align*}
        r &= \sqrt{x^2 + y^2}\\
        r^2 &= x^2 + y^2.
      \end{align*}
      This is the standard equation of a circle of radius $r$ centered
      at the origin.
    \end{enumerate}
  \end{freeResponse}
\end{question}
\mynewpage













\begin{question}
  Ellipses are also directly related to the distance formula.  Given
  two points
  \[
  (-c,0) \qquad\text{and} \qquad (c,0)
  \]
  that we will call \textbf{foci}, an \textbf{ellipse} is the set
  of points such that the sum of the distances from any point on
  the ellipse to the foci is constant.
  \begin{enumerate}      
  \item Consider an ellipse with foci:
    \[
    (-3,0) \qquad \text{and}\qquad (3,0)
    \]%\frac{x^{2}}{5^{2}}+\frac{y^{2}}{4^{2}}=1
    Which of the following points belong on the ellipse where the sum
    of the distances from any point on the ellipse to the foci is
    $10$?
    \begin{enumerate}
    \item $(3,3.2)$ % yes = 10
    \item $(-4,2.8)$ % no = 10.5124...
    \item $(4.8,0.7)$ % no = 9.76267,,
    \item $(2,-3.6666\dots)$ % yes = 10.
    \end{enumerate}
    \item Consider this drawing of an ellipse:
      \begin{center}
        \begin{tikzpicture}[geometryDiagrams,scale=.8]
          \draw (0,0) ellipse (2in and 1in);
          \draw[->,thin] (0in,-1.5in) -- (0in,1.5in);
          \draw[->,thin] (-2.5in,0in) -- (2.5in,0in);
          \filldraw[black] (2in,0) circle (2pt) node[above right] {(a,0)};
          \filldraw[black] (0,1in) circle (2pt) node[above right] {(0,b)};

          \filldraw[black] (1.73in,0in) circle (2pt) node[below left] {(c,0)};
          \filldraw[black] (-1.73in,0in) circle (2pt) node[below right] {(-c,0)};

          \draw[dashed,thin] (-1.73in,0in) -- (.9in,.89in);
          \draw[dashed,thin] (1.73in,0in) -- (.9in,.89in);

          \node at (-.75in,.5in) {$X$};
          \node at (1.2in,.35in) {$Y$};
          
          \filldraw[black] (.9in,.89in) circle (2pt);
        \end{tikzpicture}
      \end{center}
      Express $X+Y$ (as simply as you can!) in terms of $a$ and/or $b$
      and/or $c$.
    \item \textit{Geometry Giorgio} suggests that the foci of this ellipse
      \begin{center}
        \begin{tikzpicture}[geometryDiagrams,scale=.8]
          \draw (0,0) ellipse (2in and 1in);
          \draw[->,thin] (0in,-1.5in) -- (0in,1.5in);
          \draw[->,thin] (-2.5in,0in) -- (2.5in,0in);

          
          \filldraw[black] (2in,0) circle (2pt) node[above right] {(2,0)};
          \filldraw[black] (0,1in) circle (2pt) node[above right] {(0,1)};

          \filldraw[black] (1in,0in) circle (2pt) node[below] {(1,0)};
          \filldraw[black] (-1in,0in) circle (2pt) node[below] {(-1,0)};
        \end{tikzpicture}
      \end{center}
      are at $(-1,0)$ and $(1,0)$. Prove him RIGHT or prove him WRONG.
  \end{enumerate}
  \begin{freeResponse}
    \begin{enumerate}
    \item Let's see, of these
      \begin{itemize}
      \item $\sqrt{(3-3)^2+3.2^2} + \sqrt{(3+3)^2 + 3.2^2} = 10$, so this point is on the ellipse.
      \item $\sqrt{(-4-3)^2+2.8^2} + \sqrt{(-4+3)^2 + 2.8^2} \approx 10.5$, so this point is NOT on the ellipse.
      \item $\sqrt{(4.8-3)^2+0.7^2} + \sqrt{(4.8+3)^2 + 0.7^2} \approx 9.8$, so this point is NOT on the ellipse.
      \item $\sqrt{(2-3)^2+(-3.\bar{6})^2} + \sqrt{(2+3)^2 + (-3.\bar{6})^2} = 10$, so this point is on the ellipse.
      \end{itemize}
    \item Well $X+Y=2a$, as if we look at the distance from the points to $(a,0)$ we find
      \[
      2c + (a-c) + (a-c) = 2a.
      \]
    \item NO Geometry Giorgio is WRONG. The sum of the distances from
      the foci to the point $(0,1)$ should be $4$, but instead they
      are
      \[
      \sqrt{2} + \sqrt{2} = 2\sqrt{2} \ne 4.
      \]
    \end{enumerate}
  \end{freeResponse}
\end{question}
\mynewpage












\begin{question}
  Now we're going to touch on something that will come up later.
  \begin{enumerate}
  \item Suppose you have two points. SKETCH the set of points that are
    each simultaneously EQUIDISTANT from the two given points. Use a
    CONGRUENCE THEOREM to explain why your claim is correct.
  \item Now suppose you have THREE points, not in a line. How many
    points are EQUIDISTANT to each of your three points? EXPLAIN your
    reasoning.
  \item Connect three points, not all in a line, with lines to make a
    triangle. If you want a point equidistant from the vertices of the
    triangle, should you:
    \begin{itemize}
    \item Intersect the angle bisectors?
    \item Intersect the perpendicular bisectors of the sides?
    \item Something else entirely?
    \end{itemize}
    Explain your reasoning.
  \item Cool folks say that ``A circle is determined by three
    points.'' What does this mean?
  \end{enumerate}
  \begin{freeResponse}
    \begin{enumerate}
    \item Given two points, the set of points that is simultaneously
      equidistant from both is a line:
      \begin{center}
        \begin{tikzpicture}[geometryDiagrams]
          \filldraw[black] (1in,1in) circle (2pt) ;
          \filldraw[black] (0in,0in) circle (2pt) ;
          \draw[<->,dashed] (1.5in,-.5in) -- (-.5in,1.5in);
        \end{tikzpicture}
      \end{center}
      This line is the perpendicular bisector of the line connecting
      the points. We can now form two triangles, behold:
      \begin{center}
        \begin{tikzpicture}[geometryDiagrams]
          \filldraw[black] (1in,1in) circle (2pt) ;
          \filldraw[black] (0in,0in) circle (2pt) ;
          \filldraw[black] (0in,1in) circle (2pt) ;
          \draw[<->,dashed] (1.5in,-.5in) -- (-.5in,1.5in);

          \tkzDefPoint(0,0){A}
          \tkzDefPoint(1.27,1.27){M}
          \tkzDefPoint(2.54,2.54){B}
          \tkzDefPoint(0,2.54){L}
          \tkzMarkSegments[mark=|](A,M B,M)
          \tkzDrawSegment[thin](A,B)
          \tkzDrawSegment[thin](M,L)
          \tkzDrawSegments[thin](A,L B,L)
          \tkzMarkRightAngle(A,M,L)
          \tkzLabelSegment(A,L){$a$}
          \tkzLabelSegment(B,L){$b$}
        \end{tikzpicture}
      \end{center}
      By the SAS congruence theorem, with the side connecting the
      points to the midpoint, the right angle and the point on the
      line, we see that $a=b$. Hence the perpendicular bisector is the
      set of points that are equidistant from each of the two points.
    \item This is going to be a single point, as two lines intersect
      at a point! Behold:
      \begin{center}
        \begin{tikzpicture}[geometryDiagrams]
          \filldraw[black] (1in,1in) circle (2pt) ;
          \filldraw[black] (0in,0in) circle (2pt) ;
          \filldraw[black] (-1in,1in) circle (2pt) ;
          \draw[<->,dashed] (1in,0in) -- (-1in,2in);
          \draw[<->,dashed] (-1in,0in) -- (1in,2in);
        \end{tikzpicture}
      \end{center}
      The point where the dashed lines intersect is equidistant from
      each of the three points.
    \item We want to find the perpendicular bisectors of the sides and
      intersect them. This is because the set of points equidistant
      from two points lie on the perpendicular bisector, and the
      intersection of these lines will be equidistant from both.
    \item Since a circle is the set of points equidistant from a given
      point, and the point we found above is equidistant from the
      three given points, those three points lie on a circle.
    \end{enumerate}
  \end{freeResponse}
\end{question}

\end{document}
