\documentclass[noauthor,nooutcomes,handout,hints]{ximera}

\input{../preamble.tex}

\title{Sun and shadows} \author{Claire Merriman}

\begin{document}
\begin{abstract}
Tangent allows us to calculate the ratio of the legs of a right triangle.
\end{abstract}
\maketitle

\begin{listOutcomes}
\item  Recall the basic definitions of tangent.
\item Explore the differences in Sunlight throughout the year.
\item Use tangent to determine the length of shades.
\item Translate classroom mathematics into real world mathematics.
\end{listOutcomes}

%% \begin{listObjectives}
%%  \item Learn and apply basic geometric formulas,
%% \item Use trigonometry to solve common problems.
%% \end{listObjectives}

\mynewpage


\begin{definition}
 In a right triangle, \textbf{tangent} of an angle is the ratio of the length of the side opposite the angle to the length of the side adjacent to the angle. 
\end{definition}
We will use this to explore some ideas around shade and shadows.  The
path of the Sun in the sky changes throughout the year. The Sun
reaches its highest point for any given day at \textbf{solar noon;} in
the Northern Hemisphere this occurs when the Sun is due south. The Sun
reaches its highest point for the year on the \textbf{summer solstice.}

\begin{center}
 
\begin{tikzpicture}[x=.75cm,y=.75cm]
 \draw[thick] (0.2,0)--(3.2,0)--(3.2,-1.6);
 \draw[dashed] (-2.5,1.5)--(3.2,-1.6)--(3.2,-6.6)--(-2,4.97);
 \draw[thick] (3.2,-6.6)--(3.2,-9.6);
 \filldraw[color=yellow, fill=yellow, very thick](-2,4.97) circle (.5);
 \filldraw[color=yellow, fill=yellow, very thick](-2.5,1.5) circle (.5);
 \node at (1.5,.5) {overhang};
 \node[anchor=west] at (3.5, -.8) {gap between window and ceiling};
 \node[anchor=west] at (3.5, -4) {window};
 \node[anchor=west] at (3.5, -8) {height of the window from the floor};
\end{tikzpicture}
\end{center}

\mynewpage


\begin{question}
 One practice for designing south facing windows is to build an
 overhang so that
 \begin{itemize}
 \item The Sun fills the window at noon on the winter solstice.
 \item The window is completely in the shade at noon on the summer
   solstice.
 \end{itemize}
\begin{enumerate}
\item Draw a triangle that relates the angle of the Sun, the length of
  the horizontal overhang, and the length of the vertical shadow as a
  function of the solar angle and length of the overhang.
\item The maximum possible overhang length in this scenario is the one
  where the bottom of the shadow at noon on the winter solstice is at
  the top of the window. Look up the solar angle for Columbus, cite
  your source, and then find a formula relating the shadow and length
  of the overhang.
\item The minimum possible overhang length in this scenario is the one
  where the bottom of the shadow at noon on the summer solstice is at
  the bottom of the window. Look up the solar angle for Columbus, cite
  your source, and then find a formula relating the shadow and length
  of the overhang.
\end{enumerate}
\end{question}
\mynewpage


\begin{question}
 A common ceiling height is $8\ feet$, with an $16"$ gap between the top of window and the ceiling. 
 
\begin{enumerate}
 \item Find the maximum overhang length, assuming the overhang is at the top of the ceiling.
 \item Find two standard window sizes, then find the minimum overhang length and height of the window from the floor in both cases.
\end{enumerate}
\end{question}
\mynewpage

\begin{question}
 We can also use tangent to find the length of shadows from a building. For a $52\ foot$ tall building in Columbus, find:
 
\begin{enumerate}
 \item The length of the area on the on the south of the building that is in shade year round.
 \item The difference in the length of the shadow on the summer solstice and the winter solstice.
\end{enumerate}
\end{question}
\end{document}
