\documentclass[nooutcomes,noauthor,hints]{ximera}

\input{../preamble.tex}
\title{Pennies a day}

\author{Bart Snapp}

\begin{document}
\begin{abstract}
  Now we'll think about exponential growth.
\end{abstract}
\maketitle

\begin{listOutcomes}
\item SIGNIFICANT DIGITS?
\item Critique and dismantle reasonable hypotheses in regard to
  geometry and arithmetic.
\end{listOutcomes}


Again, litterally repeating ourselves: It is difficult to grasp the
size of large numbers without a context that seems real to us. We'll
use the context of ``cold, hard, cash'' and the ``cruel curse of
time'' to help us understand the magnitude of numbers.  Dream this
daydream with me:
\begin{quote}
  Suppose you were paid the following way: Just a penny on your first
  day, double that (two pennies) the next, double that (four pennies)
  the next, and so on, each day doubling the payment amount.
\end{quote}

Let's think about this seemingly impossible situation.



\mynewpage


\begin{question}
  Assume you are collecting money through the impossible situation
  above.
  \begin{enumerate}
  \item How much money would you collect in the first week? Show your
    work.
  \item \textit{Geometry Giorgio} suggest that in two weeks you would
    collect
    \[
    (\text{amount from first week}) + 2\cdot (\text{amount from first
      week})
    \]
    Is he correct? If he is correct, explain why. If he is not
    correct, explain why and give a correct analysis.
  \end{enumerate}
  \begin{freeResponse}
    \begin{enumerate}
    \item In one week, I'd collect
      \[
      0.01+0.02+0.04+0.08+0.16+0.32+0.64 = 1.27
      \]
      dollars.
    \end{enumerate}
  \end{freeResponse}
\end{question}
\mynewpage




%% TABLE
%% formula?
%% dfn of exponential growth.



\begin{question}
  Make a TABLE 
  MAKE A TABLE
  
  Suppose you want to be as rich as possible.
\end{question}
\mynewpage


\begin{question}
  FIND A FORMULA?
  
  Richter scale is a scale
  Virus
  
\end{question}



\end{document}
