\documentclass[nooutcomes,noauthor,hints]{ximera}

\input{../preamble.tex}
\title{Comparing growth}

\author{Bart Snapp}

\begin{document}
\begin{abstract}
  Now we'll compare linear and exponential growth.
\end{abstract}
\maketitle

\begin{listOutcomes}
\item 
\end{listOutcomes}


Again, literally repeating ourselves for probably a third time: It is
difficult to grasp the size of large numbers without a context that
seems real to us. We'll use the context of ``cold, hard, cash'' and
the ``cruel curse of time'' to help us understand the magnitude of
numbers.  Dream this daydream with me:
\begin{enumerate}
\item[DAYDREAM 1]
\begin{quote}
   Suppose you were paid the secondly wage of $\$1$, meaning you are
  paid a dollar \text{every second} of every minute, of every hour, of
  every day, and so on.
\end{quote}
\item[DAYDREAM 2]
  \begin{quote}
     Suppose you were paid the following way: Just a penny on your first
  day, double that (two pennies) the next, double that (four pennies)
  the next, and so on, each day doubling the payment amount.
  \end{quote}
\end{enumerate}




Let's think about this seemingly impossible situation.



\mynewpage


\begin{question}
  Assume you are collecting money through the impossible situation
  above.
  \begin{enumerate}
  \item How much money would you collect in the first week? Show your
    work.
  \item \textit{Geometry Giorgio} suggest that in two weeks you would
    collect
    \[
    (\text{amount from first week}) + 2\cdot (\text{amount from first
      week})
    \]
    Is he correct? If he is correct, explain why. If he is not
    correct, explain why and give a correct analysis.
  \end{enumerate}
  \begin{freeResponse}
    \begin{enumerate}
    \item In one week, I'd collect
      \[
      0.01+0.02+0.04+0.08+0.16+0.32+0.64 = 1.27
      \]
      dollars.
    \end{enumerate}
  \end{freeResponse}
\end{question}
\mynewpage




%% TABLE
%% formula?
%% dfn of exponential growth.



\begin{question}
  One way to conceptualize data is with a table. Fill in the table
  below:
\[
\renewcommand{\arraystretch}{3}
\begin{array}{|c||c|c|c|c|c|c|c|c|c|c|}
  \hline
  \text{Day}       & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\ \hline\hline
  \text{Collected} & \phantom{1023} & \phantom{1023}  & \phantom{1023}  & \phantom{1023}  & \phantom{1023}  & \phantom{1023}  & \phantom{1023}  & \phantom{1023}  & \phantom{1023}  & \phantom{1023}   \\ \hline
  \text{Total}     &   &   &   &   &   &   &   &   &   &    \\ \hline
\end{array}
\]
\begin{freeResponse}
  Here is my table:
  \[
\renewcommand{\arraystretch}{3}
\begin{array}{|c||c|c|c|c|c|c|c|c|c|c|}
  \hline
  \text{Day}       & 1  & 2  & 3  & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\ \hline\hline
  \text{Collected} & 0.01  & 0.02  & 0.04  & 0.08 & 0.16& 0.32& 0.64& 1.28 & 2.56  & 5.12   \\ \hline
  \text{Total}     & 0.01  & 0.03  & 0.07  & 0.15  & 0.31  & 0.63  & 1.27  & 2.55  & 5.11  & 10.23   \\ \hline
\end{array}
\]
\end{freeResponse}

  
\end{question}
\mynewpage


\begin{question}
  Now we need to REFLECT on our work.
  \begin{enumerate}
    \item Use your table above to guess a for the total amount
      collected from day $1$ to day $n$. Explain how you found your
      guess USING THE TABLE.
    \item Use ALGEBRAIC REASONING to EXPLAIN WHY your formula is true.
  \end{enumerate}
  \begin{freeResponse}
    \begin{enumerate}
      \item From the table, it looks like the amount collected from
        day $1$ to day $n$ is equal to how much you'll collect on the
        next day minus one. Since on day $n$ we collect $.01\cdot
        2^n$, we guess:
        \[
        \mathrm{Total}(n) = 0.01\cdot 2^{n+1} -0.01
        \]
      \item To see why this is true with algebra, write
        \begin{align*}
        \mathrm{Total}(n) &= 0.01 +0.01\cdot 2+0.01\cdot 2^2 +0.01 \cdot 2^3 + \dots + 0.01 \cdot 2^n\\
        &= 0.01 + 2 ( 0.01 +0.01\cdot 2+0.01\cdot 2^2 +0.01 \cdot 2^3 + \dots + 0.01 \cdot 2^{n-1})\\
        &= 0.01 + 2 ( \mathrm{Total}(n) - 0.01\cdot 2^n)\\
        &= 0.01 + 2\cdot\mathrm{Total}(n) - 0.01\cdot 2^{n+1}
        \end{align*}
    Now we have:
    \[
    \mathrm{Total}(n)= 0.01 + 2\cdot\mathrm{Total}(n) - 0.01\cdot 2^{n+1}
    \]
    Solving for $\mathrm{Total}(n)$ we find
    \[
    \mathrm{Total}(n) = 0.01\cdot 2^{n+1} -0.01.
    \]
    \end{enumerate}
  \end{freeResponse}
\end{question}



\end{document}
