\documentclass[nooutcomes,noauthor,hints]{ximera}

\input{../preamble.tex}
\title{A dollar a second}

\author{Bart Snapp}

\begin{document}
\begin{abstract}
  Let's start to think about the size of numbers.
\end{abstract}
\maketitle

\begin{listOutcomes}
\item SIGNIFICANT DIGITS?
\end{listOutcomes}


It is difficult to grasp the size of large numbers without a context
that seems real to us. We'll use the context of ``cold, hard, cash''
and the ``cruel curse of time'' to help us understand the magnitude of
numbers.  Dream this daydream with me:
\begin{quote}
  Suppose you were paid the secondly wage of $\$1$, meaning you are
  paid a dollar \text{every second} of every minute, of every hour, of
  every day, and so on.
\end{quote}

Below we will learn about numbers by exploring this daydream.



\mynewpage

\begin{question}
  How long will it take you to collect $\$100,000$? EXPLAIN using
  words, equations, and/or pictures (as helpful/needed) how you arrive
  at your conclusion and give your answer to the nearest DAY.
  \begin{freeResponse}
    Well, all we need are $100,000$ seconds to make $\$100,000$. So
    we'll divide $100,000$ (the number of seconds we need) by $60$
    (number of seconds in a minute) times $60$ (number of minutes in
    an hour) times $24$ (number of hours in a day.  Since
    \[
    \frac{100000}{60\cdot 60\cdot 24} = 1.1574\dots
    \]
    it would take us $1$ day to make around $100,000$.
  \end{freeResponse}
\end{question}
\mynewpage


%% I REALLY WANT SIGNIFICAT DIGITS.


\begin{question}
  Use your answer from the previous question to reason how much money
  you could collect in:
  \begin{enumerate}
  \item A week.
  \item A month.
  \item A year.
  \item Twenty years.
  \item A lifetime.
  \end{enumerate}
  \textbf{Round your answer from each part to $\boldsymbol{1}$ significant digit.}
  At each step, you may/should use the previous step to help. Use
  ROUGH estimates and EXPLAIN how these can all be computed without a
  calculator.
  \begin{freeResponse}
    \begin{enumerate}
      \item So if we collect around $\$100,000$ in one day, we'll
        collect around $\$700,000$ in a week as there are $7$ days in
        a week.
      \item Since there are around $4$ weeks in a month, we'll collect
        $4\cdot 700000 = 2800000$ or nearly $3$ million dollars.
      \item In a year, there are around $10$ months, and we collect
        $3$ million per month. So $30$ million dollars.
      \item In twenty years, we'll collect $30\cdot 20 = 600$ million.
      \item In a lifetime, say $100$ years, we'll collect $(600\cdot 5)$
        million, also known as $3$ billion.
    \end{enumerate}
  \end{freeResponse}
\end{question}
\mynewpage

\begin{question}
  Let's turn the last question on it's head. Use your work from the
  PREVIOUS PARTS to tell me about how long it would take to collect:
  \begin{enumerate}
  \item $1$ million dollars?
  \item $1$ billion dollars?
  \item $1$ trillion dollars?
  \item Use the INTERNET to look up the wealthiest person in the
    world. However much wealth they have.
  \end{enumerate}
  In each case, \textbf{round your answer from each part to $\boldsymbol{1}$
    significant digit} and EXPLAIN your reasoning.
  \begin{freeResponse}
    \begin{itemize}
      \item Since we collect around $\$7k$ in about a week, we'll
        collect a million in less than two weeks.
      \item Since we collect around $\$3$ billion in 100 years, it
        will take around $30$ years to collect $1$ billion dollars.
      \item A trillion is a thousand billion, so it would take around
        $30,000$ years to collect that much.
      \item Answers will vary.
    \end{itemize}
  \end{freeResponse}
\end{question}




\end{document}
