\documentclass[noauthor,nooutcomes,12pt]{ximera}

\input{../../preamble.tex}
\input{../../activityPreamble.tex}


\title{Repcount and rainbows}
\author{Bart Snapp}

\begin{document}
\begin{abstract}
  Change your code as you repeat it!
\end{abstract}
\maketitle

\nameblankgen

\begin{multicols*}{2}
  
The command \lc{repeat} might seem pretty cool, but it really comes
alive when you combine it with \lc{repcount}. On the $i$th repetition
of a \lc{repeat} command The command \lc{repcount} produces the number
$i$. We can use the command \lc{print} to witness this:
\begin{logo}
repeat 10 [ print repcount ]
\end{logo}
This produces:
\begin{logoout}
\end{logoout}

  
\section{Commands to know}
\begin{tabular}{lll}
  \lc{CMD}   & Description                 \\ \hlinewd{1pt}
  \lc{repcount} & tells you which repetition  \\
  \lc{print \#}     & prints \lc{\#}
\end{tabular}


\end{multicols*}

\newpage

\begin{problem}
  Above, there is code that draws a flower. Explain in words what each
  line of the code does.
\end{problem}

\newpage

\begin{problem}
  Make a command \lc{flower} that will make a small version ($\sim 50$
  units tall) of the flower above.  Show your code and your picture.
\end{problem}

\newpage


\begin{problem}
  What direction is the turtle facing after your flower command is
  made? Explain how you know with words/pictures.
\end{problem}

\newpage

\begin{problem}
  Make a command \lc{patch} that will make a `patch' of three flowers
  in a row.  Show your code and your picture. 
\end{problem}

\newpage

\begin{problem}
  Make a command \lc{field} that will produce a field of color
  \lc{[80 100 80]} covered in patches of flowers. Show your
  code and your picture.
\end{problem}


\end{document}
