\documentclass[noauthor,hints,nooutcomes,handout]{ximera}

\input{../preamble.tex}

\title{Circles of all sizes}
\author{Claire Merriman \and Bart Snapp}

%% ONLY REQUIRES WHAT's YOUR ANGLE...



\begin{document}
\begin{abstract}
  We'll explore some more properties of circles.
\end{abstract}
\maketitle

\begin{listOutcomes}
  \item Think about the isoperimetric inequality.
\item Use radians to find the length of a circle segment.
\item Use formulas to solve word problems.
\end{listOutcomes}

%% \begin{listObjectives}
%% \item Learn and apply basic geometric formulas,
%% \item Explain why presented concepts and formulas are true,
%% \end{listObjectives}


\mynewpage

\begin{question}
  I was reading some fancy math the other day, it said for any shape
  of area $A$, the perimeter of this shape is $P$ where:
  \[
  P \ge 2\pi\sqrt{A/\pi}
  \]
  Use the fact that a circle is the two dimensional shape of greatest
  area for a given perimeter to deduce the inequality above.
  \begin{hint} Recall $A = \pi r^2$ and $C = 2\pi r$.
  \end{hint}
\end{question}
\mynewpage




\begin{question}
\textbf{Radians} are a way to measure angles that connect the radius
of a circle to its perimeter. $1 \ radian$ is the \textbf{angle made}
when we \textbf{wrap a radius around the perimeter of a circle.} On a
circle with radius $1\ unit$, the length of the thick arc is also
$1\ unit$, so the marked angle has measure $1 \ radian$.


\begin{center}
\begin{tikzpicture}[geometryDiagrams]
  \tkzDefPoint(0,0){O}
  \tkzDefPoint(4,0){A}
  \tkzDefPoint(4*cos(1),4*sin(1)){B}
  \tkzDrawArc[line width = 4,black](O,A)(B)
  \tkzDrawArc[](O,B)(A)
  \tkzDrawLines[add = 0 and .5](O,A O,B)
 % \tkzLablSegments[mark=|](O,A)
  \tkzDrawPoints(O,A,B)
  \tkzMarkAngle[size=0.75cm,mark=](A,O,B)
   \tkzLabelAngle[pos = .8,right](A,O,B){$\theta=1\ rad$}
 \end{tikzpicture}
 
\end{center}

The ever insightful Louie Llama is here to help!

\begin{enumerate}
    \item Louie Llama walks all the way around the  the circle. When he gets back to where he started, he has turned $2\pi \ rad$. Explain why in your own words. 
    \item What is the length of thick segment if $\theta=\pi \ rad$? Why?
    \item What is the length of the thick segment if $\theta=1 \ rad$ and the radius is $r$? Explain your reasoning.
\end{enumerate}
\end{question}
\mynewpage












\begin{question} %% https://en.wikipedia.org/wiki/String_girdling_Earth 
  Here a problem that is at least $300$ years old, so let's call it an  ``oldie, but a goodie!''
  \begin{quote}
    Imagine a chain, pulled tight around the Earth's equator. Suppose
    you add an extra $10'$ to the chain. The chain is then raised up
    uniformly, all around the Earth, as high as possible. How high is
    that?
  \end{quote}
  Supposing that
  \begin{itemize}
  \item There are $5280$ feet in a mile, and
  \item the radius of the Earth is $4000$ miles,
  \end{itemize}
  it is now time for you to try you hand at this classic.
  \begin{enumerate}
  \item Give a solution in feet. Show all work.
  \item Now solve the problem AGAIN but for a table that is $2'$ in
    radius; that is imagine a chain, pulled tight around a circular
    table. Suppose you add an extra $10'$ to the chain. The chain is
    then pulled away uniformly, all around the table, as far as
    possible. How far is that?
  \item Is the answer to the previous parts surprising? Explain why or
    why not.
  \end{enumerate}
\end{question}

\end{document}
