\documentclass[noauthor,nooutcomes,12pt]{ximera}

\input{../../preamble.tex}
\input{../../activityPreamble.tex}


\title{Basic shapes}
\author{Bart Snapp}

\begin{document}
\begin{abstract}
Let's get started with \LOGO.
\end{abstract}
\maketitle

\nameblankgen

\begin{multicols}{2}
\LOGO~is a fun programming language where you help a ``drawing
turtle'' create beautiful pictures. That is, there is this turtle,
\turtle, who loves nothing more than drawing pictures with
you. \LOGO~is quite old and there are many flavors. We suggest
\logoFlavor, though you do you.

Your shelled friend could look more like a turtle than \turtle, but
she's still a turtle. The turtle
\[
\turtle
\]
is standing with her ``head'' pointing up. If she moves forward, she
will move up.  To guide the turtle around, you give it directions like
\lc{fd 100} to mean ``forward 100 units'' in which case you will see
something like:
\begin{logoout}
\begin{tikzpicture}[turtle/distance=2cm]
  \draw [thick,black,turtle={home,forward}];
  \node at (0,2) {\turtle};
\end{tikzpicture}
\end{logoout}
Remember, she's a drawing turtle, drawing a path wherever she goes.

To help her turn, use a command like and \lc{lt 90} to mean ``turn
$90$ degrees to the left.'' So for example, the code below draws a
square:

\begin{logo}
fd 100
lt 90
fd 100
lt 90
fd 100
lt 90
fd 100
\end{logo}
\begin{logoout}
\begin{tikzpicture}[turtle/distance=2cm]
  \draw [thick,black,turtle={home,forward,left,forward,left,forward,left,forward}];
  \node at (0,0) {\turtler};
\end{tikzpicture}
\end{logoout}

Note, now she has turned, and is pointing directly right, like
$\turtler$, thus proving the old adage,
\begin{quote}
  Two wrongs don't make a right, but four lefts do.
\end{quote}
\end{multicols}

\newpage

\begin{problem}
  Use the techniques above to help the turtle draw an equilateral
  triangle with side length $250$. Show your code and your picture.
\end{problem}

\newpage

\begin{problem}
  Use the techniques above to help the turtle draw a regular pentagon
  triangle with side length $90$. Show your code and your picture. 
\end{problem}

\newpage


\begin{problem}
  Use the techniques above to help the turtle draw an regular hexagon
  with side length $80$. Show your code and your picture. 
\end{problem}

\newpage

\begin{problem}
  Use the techniques above to help the turtle draw a regular
  five-pointed star of a reasonable size. Show your code and your
  picture.
\end{problem}



\end{document}
