\documentclass[noauthor,nooutcomes,12pt]{ximera}

\input{../../preamble.tex}
\input{../../activityPreamble.tex}


\title{Basic directions}
\author{Bart Snapp}

\begin{document}
\begin{abstract}
Let's get started with \LOGO.
\end{abstract}
\maketitle

\nameblankgen

\begin{multicols*}{2}
\LOGO~is a fun programming language where you help a ``drawing
turtle'' create beautiful pictures. That is, there is this turtle,
\turtle, who loves nothing more than drawing pictures with
you. \LOGO~is quite old and there are many flavors. We suggest
\logoFlavor, though you do you.

Your shelled friend could look more like a turtle than \turtle, but
they're still a turtle. The turtle
\[
\turtle
\]
is standing with their ``head'' pointing up. If the turtle moves
forward, they will move up.  To guide the turtle around, you give it
directions like \lc{fd 100} to mean ``forward 100 units'' in which
case you will see something like:
\begin{logoout}
\begin{tikzpicture}[turtle/distance=2cm]
  \draw [thick,black,turtle={home,forward}];
  \node at (0,2) {\turtle};
\end{tikzpicture}
\end{logoout}
Remember, they are a drawing turtle, drawing a path wherever they go.

To help them turn, use a command like \lc{rt 60} to mean ``turn $60$
degrees to the right and \lc{lt 90} to mean ``turn $90$ degrees to the
left.''


\columnbreak

We can put these commands together to draw a square:


\begin{logo}
fd 100
lt 90
fd 100
lt 90
fd 100
lt 90
fd 100
\end{logo}
\begin{logoout}
\begin{tikzpicture}[turtle/distance=2cm]
  \draw [thick,black,turtle={home,forward,left,forward,left,forward,left,forward}];
  \node at (0,0) {\turtler};
\end{tikzpicture}
\end{logoout}

Note, now the turtle has turned, and is pointing directly right, like
$\turtler$, thus proving the old adage,
\begin{quote}
  Two wrongs don't make a right, but four lefts do.
\end{quote}

\section{Commands to know}
\begin{tabular}{lll}
  \lc{CMD}   & Description                 &  \lc{EG} \\ \hlinewd{1pt}
  \lc{fd \#} & Move forward \lc{\#} units  &  \lc{fd 78}\\
  \lc{bk \#} & Move backward \lc{\#} units & \lc{bk 96}\\
  \lc{rt \#} & Turn right \lc{\#} degrees  & \lc{rt 72}\\
  \lc{lt \#} & Turn left  \lc{\#} degrees  & \lc{lt 61}\\
  \lc{home}  & Reset the turtle            & \lc{home}\\
  \lc{cs}    & Clear the screen and send home            & \lc{cs}\\
  \lc{pu}    & Pen-up, stop drawing        & \lc{pu}\\
  \lc{pd}    & Pen-down, start drawing     & \lc{pd}\\
\end{tabular}

  
\end{multicols*}

\newpage

\begin{problem}
  Use the techniques above to help the turtle draw an equilateral
  triangle with side length $250$. Show your code and your picture.
\end{problem}

\newpage

\begin{problem}
  Use the techniques above to help the turtle draw a regular pentagon
  triangle with side length $90$. Show your code and your picture. 
\end{problem}

\newpage


\begin{problem}
  Use the techniques above to help the turtle draw a regular hexagon
  with side length $80$. Show your code and your picture.
\end{problem}

\newpage

\begin{problem}
  Use the techniques above to help the turtle draw a regular
  five-pointed star of a reasonable size. Show your code and your
  picture.
\end{problem}

\newpage

\begin{problem}
  Use the techniques above to draw the rep-4-tile known as the sphinx,
  that is, produce this picture:
  \begin{logoout}
\begin{tikzpicture}[turtle/distance=2cm]
  \draw [thick,black,turtle={home,right,forward,forward,forward,left=120,forward,left=60,forward,right=60,forward,left=120,forward,forward}];
  %\node at (0,0) {\rotatebox{140}{\turtle}};
\end{tikzpicture}
\end{logoout}

  Show your code and your
  picture.
\end{problem}



\end{document}
