\documentclass[noauthor]{ximera}

\input{../preamble}

\author{Bart Snapp}

\checkYourselfAbstract

\begin{document}
\maketitle


\begin{exercise}
  About how many seconds are in a day?
\end{exercise}


\begin{exercise}
  Suppose you can read one book a week. How many books could you read
  in a lucky, healthy, lifetime?
  \begin{multicols}{2}
  \begin{enumerate}
  \item Hundreds?
  \item Thousands?
  \item Tens of thousands?
  \item Millions?
  \item Tens of millions?
  \item Hundreds of thousands?
  \end{enumerate}
  \end{multicols}
\end{exercise}


\begin{exercise}
  Suppose a library has one-hundred thousand books.  If you could read
  one book every week, how long would it take to read every book in
  this library?
  \begin{multicols}{2}
  \begin{enumerate}
  \item Days?
  \item Years?
  \item Decades?
  \item Centuries?
  \item Millennia?
 \end{enumerate}
 \end{multicols}
\end{exercise}


\begin{exercise}
  The \textit{New Horizons} spacecraft is the fastest yet to leave the
  solar system. It is traveling at around $10$ miles per second.
A light-year is about $6$ trillion miles.  Roughly how long would it for 
  \textit{New Horizons} to travel one light-year?
  \begin{multicols}{2}
  \begin{enumerate}
  \item Years?
  \item Decades?
  \item Centuries?
  \item Millennia?
  \item Tens of millennia?
 \end{enumerate}
 \end{multicols}
\end{exercise}


\begin{exercise}
  A TV episode lasts 45 minutes. About how many episodes can you watch in 24 hours? 
  (Assuming you don't take breaks).
  \begin{multicols}{2}
  \begin{enumerate}
    \item Around 20
    \item Around 30
    \item Around 40
    \item Around 50
   \end{enumerate}
    \end{multicols}
\end{exercise}

\answerlistbox{$\sim100,000$}{(b)}{(e)}{(e)}{(b)}
\end{document}
