\documentclass[nooutcomes,noauthor,hints]{ximera}

\input{../preamble.tex}
\title{Hip to be square}

\author{Bart Snapp}

\begin{document}
\begin{abstract}
  We extend scaling ideas from squares and cubes to arbitrary shapes.
\end{abstract}
\maketitle

\begin{listOutcomes}
\item 
\end{listOutcomes}




\mynewpage


\begin{question}
  Let's think about scaling squares and cubes.
  \begin{enumerate}
  \item Scale a square by a scale factor of $3$. What's the area of the new square? 
  \item Scale a square by a scale factor of $x$. What's the area of the new square?
  \item Scale a cube by a scale factor of $3$. What's the volume of the new cube?
  \item Scale a cube by a scale factor of $x$. What's the volume of the new cube?
  \item Scale a cube by a scale factor of $x$. What's the area of one face of the new cube?
  \item Scale a cube by a scale factor of $x$. What's the surface area of the new cube?
  \end{enumerate}
  In each case above, DRAW PICTURES to help you EXPLAIN why your
  answer is correct.
\end{question}
\mynewpage



\begin{question}
  We know how squares and cubes scale, but what about weird shapes?
  Louie Llama can help us out here.  Consider this picture:
  \begin{center}
    picture of llama in square being zoomed to another llama in the square.
  \end{center}
  Let\index{Louie Llama}
  \begin{align*}
    L &= \text{Area of Louie Llama}\\
    S &= \text{Area of Square}\\
    B &= \text{Area of bigger llama, Blouie Llama}.
  \end{align*}
  \begin{enumerate}
  \item If $x$ is the scale-factor, explain why:
    \[
    \frac{L}{S} = \frac{B}{x^2 S}
    \]
  \item Solve for $B$ above, and explain how this demonstrates how
    scaling and area work together.
  \end{enumerate}
  
\end{question}
\mynewpage


\begin{question}
 
\end{question}



\end{document}
