\documentclass[noauthor,nooutcomes,handout]{../ximera}

\input{../preamble.tex}

\title{A few more triangles}
\author{Claire Merriman}

%% ONLY REQUIRES WHAT's YOUR ANGLE...



\begin{document}
\begin{abstract}
We'll explore some more properties of angles and triangles.\end{abstract}
\maketitle

\begin{listOutcomes}
\item Explain the relationship between vertical and supplementary angles,
\item State and triangle congruence,
\item Use radians to find the length of a circle segment,
\item Use formulas to so word problems.
\end{listOutcomes}

\begin{listObjectives}
\item Learn and apply basic geometric formulas,
\item Explain why presented concepts and formulas are true,
\end{listObjectives}
\mynewpage




In the following diagram, the lines $\bar{AB}$ and $\bar{CF}$ are parallel and perpendicular to $\bar{AC}$. Suppose that $\left\vert AE\right\vert =\left\vert
EB\right\vert $ and $\left\vert CE\right\vert =\left\vert
ED\right\vert $.

This diagram is used for two questions.
\begin{center}
\begin{tikzpicture}[rotate=15]
  \coordinate (A) at (-2,0);
  \coordinate (B) at (6,0);
  \coordinate (C) at (-2,-4);
  \coordinate (D) at (6,4);
  \coordinate (E) at (2,0);
  \coordinate (F) at (8,-4);
  \coordinate (G) at (-4,0);
  \coordinate (H) at (8,0);
  \coordinate (I) at (-4,-4);
  \draw (G)--(H);
  \draw (I)--(F);
  \draw (B)--(D)--(C)--(A);
  \tkzLabelPoints[above](D,A,E)
  \tkzLabelPoints[below](B,C,F)
  \tkzMarkSegments[mark=|](A,E E,B)
  \tkzMarkSegments[mark=||](C,E E,D)
  \tkzMarkAngle[size=0.75cm,mark=](B,E,D)
  \tkzMarkAngle[size=0.5cm,mark=](D,E,A)
  \tkzMarkAngle[size=0.75cm,mark=](A,E,C)
  \tkzMarkAngle[size=0.5cm,mark=](C,E,B)
  \tkzMarkAngle[size=0.75,mark=](F,C,D)
  \tkzLabelAngle[pos = -1](A,E,C){$\alpha$}
  \tkzLabelAngle[pos = 1](C,E,B){$\beta$}
  \tkzLabelAngle[pos = 1](D,E,A){$\gamma$}
  \tkzLabelAngle[pos = -1](C,E,A){$\delta$}
  \tkzLabelAngle[pos = 1](F,C,D){$\epsilon$}
\end{tikzpicture}
\end{center}
\begin{question}
\begin{enumerate}
    \item Find $\beta,\gamma,\delta$ and $\epsilon$ in terms of $\alpha$. Explain your reasoning. 
    \item Look up triangle congruence theorems and cite your sources. Explain why $\left\vert AC\right\vert =\left\vert
BD\right\vert $.
    \item Explain why $\left\vert AC\right\vert =\left\vert
BD\right\vert $ does not require $\bar{AB}$ and $\bar{AC}$ to be perpendicular.
\end{enumerate}
\end{question}
\mynewpage

\begin{question}
\textit{Radians} are another way to measure angles. $1 \ radian$ is the angle made when we take the radius
and wrap it round the circle. On a circle with radius $1\ unit$, the length of the blue arc is also $1\ unit$, so the marked angle has measure $1 \ radian$.


\begin{center}
\begin{tikzpicture}[geometryDiagrams]
  \tkzDefPoint(0,0){O}
  \tkzDefPoint(4,0){A}
  \tkzDefPoint(4*cos(1),4*sin(1)){B}
  \tkzDrawArc[blue,thick](O,A)(B)
  \tkzDrawArc[thick](O,B)(A)
  \tkzDrawLines[add = 0 and .5](O,A O,B)
 % \tkzLablSegments[mark=|](O,A)
  \tkzDrawPoints(O,A,B)
  \tkzMarkAngle[size=0.75cm,mark=](A,O,B)
   \tkzLabelAngle[pos = 1.5](A,O,B){$\theta=1\ rad$}
 \end{tikzpicture}
 
\end{center}

The ever insightful Louie Llama is here to help!

\begin{enumerate}
    \item Louie Llama walks all the way around the  the circle. When he gets back to where he started, he has turn $2\pi \ rad$. Explain why in your own words. 
    \item What is the length of blue segment if $\theta=\pi \ rad$? Why?
    \item What is the length of the blue segment if $\theta=1 \ rad$ and the radius is $r$? Explain your reasoning.
\end{enumerate}
\end{question}
\mynewpage

\begin{question}
  Here a problem that is at least $300$ years old, so let's call it an  ``oldie, but a goodie!''
  \begin{quote}
    Imagine a chain, pulled tight around the Earth's equator. Suppose
   you add an extra $10'$ to the chain. The chain is then raised up
    uniformly, all around the Earth, as high as possible. How high is    that?
  \end{quote}
  Supposing that
  \begin{itemize}
  \item There are $5280$ feet in a mile, and
  \item the radius of the Earth is $4000$ miles,
  \end{itemize}
  it is now time for you to try you hand at this classic.
  \begin{enumerate}
  \item Give a solution in feet. Show all work.
  \item Is the answer surprising? Explain why you say yes or no.
  \end{enumerate}
\end{question}

\end{document}
