\documentclass[noauthor,nooutcomes]{ximera}

\input{../preamble}

\author{Bart Snapp}

\checkYourselfAbstract

\begin{document}
\maketitle


\begin{exercise}
  You've been hired by the LEGO corporation to make a large helium
  balloon in the shape of a minifigure. If the LEGO minifigure balloon
  is
\begin{itemize}
    \item around $21$ meters tall,
    \item around $15$ meters wide,
    \item around $10$ meters deep,
\end{itemize}
and
\begin{itemize}
\item the fabric needed to make the balloon has a mass of $0.2$ kilograms per square meter.
\end{itemize}
What's the most reasonable estimate for the mass of the EMPTY
(deflated) helium balloon?
\begin{enumerate}\begin{multicols}{2}
  \item $3$ kilograms
  \item $30$ kilograms
  \item $300$ kilograms
  \item $3000$ kilograms
  \end{multicols}
\end{enumerate}
\end{exercise}





\begin{exercise}
  Suppose you've designed a concrete statue of a LEGO minifigure.  How
  much more will the statue weigh if it's linear dimensions (length,
  height, width) are increased by $20\%$?
  \begin{enumerate}\begin{multicols}{2}
    \item Around $20\%$
    \item Around $30\%$
    \item Around $40\%$
    \item Around $50\%$
    \item Around $60\%$
    \item Around $70\%$
    \end{multicols}
  \end{enumerate}
\end{exercise}

\begin{exercise}
  You've designed a large helium balloon in the shape of a LEGO
  minifigure. How much more fabric will be needed if the linear
  dimensions (length, height, width) are increased by $15\%$?
  \begin{enumerate}\begin{multicols}{2}
    \item Around $10\%$
    \item Around $20\%$
    \item Around $30\%$
    \item Around $40\%$
    \item Around $50\%$
    \end{multicols}
  \end{enumerate}
\end{exercise}






\begin{exercise}
  After doing all this work for LEGO, they have given you a coupon for
  $15\%$ off your next LEGO purchase. Of course, there is sales tax of
  around $6\%$.  You want to buy a commemorative ``giant'' LEGO
  minifigure.

  In order to save the most money, do you want them to:
  \begin{itemize}
  \item add the tax and then take the discount, or
  \item take the discount and then add the tax?
  \end{itemize}
  \begin{enumerate}\begin{multicols}{2}
  \item It depends on the cost of the item.
  \item It doesn't matter which you compute first.
  \item Add the tax first, then take the discount to save the most money.
  \item Take the discount, then add the tax to save the most money.
    \end{multicols}
  \end{enumerate}
\end{exercise}



\begin{exercise}
  You want to buy something that costs $\$9.99$. You have a coupon for
  $\%10$ off, but in your city, sales tax is $\%10$. Which of the
  following is true:
  \begin{enumerate}
    \item After the coupon and tax are applied, you owe less than
    $\$9.99$.
    \item After the coupon and tax are applied, you owe exactly
      $\$9.99$.
    \item After the coupon and tax are applied, you owe more than
      $\$9.99$.
    \item There is insufficient information to solve this problem.
  \end{enumerate}
\end{exercise}



\answerlistbox{(c)}{(f)}{(c)}{(b)}{(a)}
\end{document}
