\documentclass[nooutcomes,noauthor,hints,handout,12pt]{ximera}

\input{../preamble.tex}
\title{Borda blues and other impossibilities}

\author{Bart Snapp}

\begin{document}
\begin{abstract}
  The subtleties of voting are strange.
\end{abstract}
\maketitle

\begin{listOutcomes}
\item Critically analyze data.
\item Witness subtleties of voting systems through examples.
\item Accommodate new knowledge from a primary source. 
\end{listOutcomes}



\mynewpage

\begin{question}
The Borda Count is pretty cool, but it does have some flaws. One of
which is that adding irrelevant candidates can change the result of an
election. Consider our \mooculus~apartment election. What if we add an additional candidate $X$ where:

\begin{itemize}
\item $16$ residents prefer dogs, better than cats, better than no pets at all, better than $X$.
\item $4$ residents prefer cats, better than dogs, better than no pets at all, better than $X$.
\item $18$ residents prefer no pets at all, better than $X$, better than cats, better
  than dogs.
\end{itemize}
Now answer these questions:
\begin{enumerate}
\item Who wins the Borda Count before candidate $X$ is introduced?
\item Who wins the Borda Count after candidate $X$ is introduced? (note,
  now the options are awarded $3,2,1,0$ points)
\item Did any of the residents change their \textbf{order of preference} in
  regards to your answers in the two questions above?
\item Why is this strange? Demonstrate understanding through your
  explanation.
\end{enumerate}
\end{question}
\mynewpage







\begin{question}
  In the mid 20th century, Kenneth Arrow proved the following theorem in his doctoral thesis.
 \begin{mdframed}[style=OutcomeStyle]
  \begin{quote}
    Suppose that there is a voting system where:
    \begin{itemize}
    \item If we exclude all candidates except for $X$ and $Y$, then
      the groups preference for $X$ and $Y$ should be unchanged when
      all candidates are considered. This is known as \textit{Pareto
        Efficiency}.
    \item If voters prefer $X$ to $Y$, and more candidates are added
      with their rankings interleaved with the previous, the groups
      preference of $X$ to $Y$ is unchanged. This is known as
      \textit{Independence of Irrelevant Alternatives}.
    \end{itemize}
    \textbf{Arrow's theorem} says that in this case,
    there is a single voter who can manipulate the entire result of
    the election, simply by changing their own vote.  That voter is
    referred to as the ``dictator.''
  \end{quote}
 \end{mdframed}
This theorem is a bit difficult to understand, so let's think in terms
of our example:
\begin{itemize}
\item $16$ residents prefer dogs, better than cats, better than no pets at all.
\item $4$ residents prefer cats, better than dogs, better than no pets at all.
\item $18$ residents prefer no pets at all, better than cats, better
  than dogs.
\end{itemize}
In particular, we'll explore why the theorem does NOT apply for the cases we consider. 
\begin{enumerate}
\item Who wins if the only options were cats versus dogs? What about
  cats versus no pets?
\item Explain why Arrow's theorem does \textbf{not apply to Plurality Voting} and
  why Arrow's theorem does \textbf{not apply to Instant Run-Off Voting}.
\item Now explain why Arrow's theorem does \textbf{not apply to the Borda Count}.
\end{enumerate}

\end{question}
\mynewpage



\begin{question}
  Arrow's theorem is often called an ``impossibility'' theorem because it
  can be stated as:
  \begin{quote}
    It's impossible to have a voting scheme that is Pareto Efficient,
    Independent of Irrelevant Alternatives, with no dictators.
  \end{quote}
  Not to be outdone, Professor Mixon of The Ohio State University
  coauthored the following paper: \link[\textit{An Impossibility
      Theorem for
      Gerrymandering}]{https://www.tandfonline.com/doi/full/10.1080/00029890.2018.1517571}.


  Explain the statement of this so-called impossibility theorem for
  gerrymandering in an accurate, but easy to understand way, in your
  own words. To do this correctly you'll need to be specific and
  explain quite a bit. However, all the answers are in Mixion and
  Alexeev's paper, and you are more than equipped to find them!
  \begin{hint}
    As part of your explanation, you will need to use/define/explain
    the terms: Districting system; one person, one vote; Polsby-Popper
    compactness; isoperimetric; bounded efficiency gap.
  \end{hint}
\end{question}





\end{document}
