\documentclass[handout,nooutcomes,noauthor,12pt]{ximera}

\input{../preamble.tex}
\title{Estimates and formulas}

\author{Bart Snapp}

\begin{document}
\begin{abstract}
Let's think about estimates and formulas
\end{abstract}
\maketitle


\begin{listSectionOutcomes}
  % \item{Edit/create PDFs to create completed journal entries.}
  % \item{Hand-in journal entries online.}
  \item{Work in nonstandard units.}
  \item{Estimate areas and volumes in nonstandard units.}
  \item{Critique and dismantle reasonable hypotheses in regard to geometry and arithmetic.}
  \item Critically analyze a diagram.
\item Know conventions and definitions to be used in later problems.
\item Estimate in standard units.
\item Distinguish between reasonable and unreasonable estimates.
\item Determine a reasonable estimate before preforming a calculation.
\item Give the standard formula for the area of a triangle.
\item Explain Cavalieri's principle.
\item Explain why the formula for the area of a triangle is true.
\item Explain how shapes of the same area can have drastically
  different perimeters.
  \item Dissect a cube into three right pyramids.
\item Find the volume of right pyramid.
\item State Cavalieri's shearing principle in three dimensions.
\item Apply Cavalieri's shearing principle to derive the volume of ANY pyramid
  of height $s$ over an $s\times s$ square base.
\item Explain how shapes of the same volume can have drastically
  different surface areas.
\item Apply the distributive property in a geometric setting.
\item Apply basic geometric formulas.
\end{listSectionOutcomes}



% Measurements of length, area, and volume
% computing how  scaling effect length, area, and volume
% Conceptualizing the effect of scaling on  length, area, and volume
% implications of scaling  length, area, and volume to other measurable quantaties
% witnessing the effects of scaling in real life.
% understnaing that scaling does not solve all problems.



\end{document}
