\documentclass[handout,nooutcomes,noauthor]{ximera}
\input{../preamble.tex}
\title{Introduction}

\author{Bart Snapp}

\begin{document}
\begin{abstract}
  Let's get started.
\end{abstract}
\maketitle





Welcome to this transformative journey in geometry, a course designed
not just to teach but to actively engage you in the learning
process. This Applied Geometry Journal, an innovative creation of
educators at The Ohio State University, has been enriched by the
contributions over many years. Most importantly, it includes a crucial
contributor---YOU!






\subsection*{Our goals and your role}


In this course, we aim to:
\begin{enumerate}
\item Reinforce foundational mathematics and support the mathematics needed for advanced concepts.
\item Help students make fewer mistakes while learning to discover mathematics independently.
\item Translate classroom mathematics into real-world mathematics.
\item Encourage you to question, critique, and dismantle reasonable
  hypotheses in geometry and arithmetic.
\item Make the learning process enjoyable and engaging.
\end{enumerate}


On the other hand, you play a role to as an active learner. We believe
in the maxim: ``It is best to learn by doing.'' This course is
structured to help you apply mathematical lessons from one context to
another, each time revealing a different aspect of the situation. You
will learn to strip solutions of extraneous details and apply concepts
in new, varied contexts; this is the essence of understanding.

Your job is to \textbf{demonstrate understanding} through your
answers. You will do this by explaining your work and your ideas.
Your target audience is your peers—fellow students in this class. Your
explanations should be clear, specific, and insightful, demonstrating
your own understanding without overwhelming your readers. Your goal is
to enlighten, not to obscure.



\subsection*{The art of explanation}

To excel in this course, it's vital to adopt a reflective approach to
learning:
\begin{description}
\item[Explain with Clarity:] When you explain a mathematical concept, imagine you're teaching a fellow student. Your explanation should be straightforward, using language and examples that resonate with your peers.
\item[Be Convincing:] Show your understanding through detailed explanations. Your task is to make complex ideas accessible, not to transfer the burden of understanding to your reader.
\item[Reflect and Review:] After completing a problem, take a step back. Return to it later with fresh eyes and critically assess your solution. Ask yourself:
  \begin{itemize}
        \item Have I addressed all aspects of the problem?
        \item Do the numbers and results logically make sense?
        \item Can I validate my results through a quick approximation
          or an alternative method?
  \end{itemize}
\end{description}

\subsection*{Seeking help and collaborative learning}

It's natural to encounter challenges or to question your solutions. In
such moments, don't hesitate to seek help. Articulate your process and
understanding, and openly discuss where you feel uncertain. Often, the
errors you encounter are common and discussing them can lead to
valuable insights for the entire class. Remember, \textbf{every
  mistake is a learning opportunity for everyone.}





\subsection*{Authors of this journal}

This ``geometry journal'' was created by Dr.\ Claire Merriman,
Dr.\ Jenny Sheldon, and Dr.\ Bart Snapp at The Ohio State
University. Additional content was developed/inspired by the work of
Dr.\ Betsy McNeal, Dr.\ Vic Ferdinand, Dr.\ Bradford Findell, and
Dr.\ Herbert Clemens.


And of course, there is \textbf{one more
  content creator} in this Journal, \textbf{YOU!}

\end{document}
