\documentclass[noauthor,nooutcomes]{ximera}

\input{../preamble}

\author{Bart Snapp}

\checkYourselfAbstract

\begin{document}
\maketitle







\begin{exercise}
 At a certain publisher, the cost of the ``hard cover'' of a
 hard-bound book, dominates the cost of producing the book. If we
 \textbf{double the lengths of the sides} of the book, how much more do we expect the
 book to cost?
 \begin{enumerate}
   \begin{multicols}{2}
   \item Twice as much.
   \item Four times as much.
   \item Six times as much.
   \item Eight times as much.
   \end{multicols}
 \end{enumerate}
\end{exercise}


\begin{exercise}
  Box shaped glass aquariums come in various sizes. How do you expect
  the price of a glass aquarium to scale?  \textbf{Select all that
    apply:}
 \begin{enumerate}
   \begin{multicols}{2}
   \item Like the diagonal of opposite corners.
   \item Like the surface area of the aquarium.
   \item Like the volume of the aquarium.
   \item None of the above.
   \end{multicols}
 \end{enumerate}
\end{exercise}



\begin{exercise}
  Go look up how the price of pizza's scale. What do you find?
 \begin{enumerate}
   \begin{multicols}{2}
   \item Like the diameter.
   \item Like the surface area.
   \item Like the volume.
   \end{multicols}
 \end{enumerate}
\end{exercise}





\begin{exercise}
  Literally billions of \textit{iPhones} have been sold. How does the
  price of the \textit{iPhone} scale?
\textbf{Select all that apply:}
 \begin{enumerate}
   \begin{multicols}{2}
   \item Like the diagonal of the screen.
   \item Like the area of the screen.
   \item Like the volume of the phone.
   \item None of the above.
   \end{multicols}
 \end{enumerate}
\end{exercise}


\begin{exercise}
  At a small mattress factory, the cost of the mattress is roughly
  proportional to the cost of the raw materials. When pricing the
  mattresses, the owners should scale the price\dots~
\textbf{Select all that apply:}
 \begin{enumerate}
   \begin{multicols}{2}
   \item Like the diagonal of the mattress.
   \item Like the area of the mattress.
   \item Like the volume of the mattress.
   \item None of the above.
   \end{multicols}
 \end{enumerate}
\end{exercise}




\answerlistbox{(b)}{(b)}{(a)}{(d)}{(b) and (c)}
\end{document}
