\documentclass[handout,noauthor,nooutcomes,hints,12pt]{ximera}
\input{../preamble.tex}
\title{Getting started}
\author{Claire Merriman and Bart Snapp}

\begin{document}
\begin{abstract}
  We make estimates of numbers of objects in every-day settings and we
  observe the effects of scaling when we change objects.
\end{abstract}
\maketitle

%% \begin{listObjectives}
%%  \item{Determine a reasonable estimate before preforming a calculation.}
%%  \item{Increase student confidence in their ability to solve difficult math problems by using previous results, trying different methods, asking questions, and work- ing with others.}
%% \end{listObjectives}

\begin{listOutcomes}
  \item{Edit/create PDFs to create completed journal entries.}
  \item{Hand-in journal entries online.}
  \item{Communicate mathematical ideas.}
  \item{Work in nonstandard units.}
  \item{Estimate areas and volumes in nonstandard units.}
  \item{Critique and dismantle reasonable hypotheses in regard to geometry and
              arithmetic.}
\end{listOutcomes}

\mynewpage

\begin{question}
  Here's a scale picture of a large \textit{Happy Fun Ball}:
  \begin{center}
    \begin{tikzpicture}
      % Define the radius of the circle (half of the diameter)
      \def\ballradius{4.7cm} % 

      % Draw the circle
      \draw[ultra thick] (0, 0) circle (\ballradius);

      % You can add additional elements or labels here if needed
    \end{tikzpicture}
  \end{center}
  Look around the room you are in. How many large \textit{Happy Fun Balls}
  would it take to:
  \begin{enumerate}
    \item Line one edge of the room?
    \item Cover the floor?
    \item Fill the room?
  \end{enumerate}
  Answer these questions by using the scale picture above and your actual classroom. \textbf{You will need to stand up and walk around the room to make your estimates.}
  In each case, EXPLAIN what you did using words and pictures/diagrams. Moreover, explain how you used your work to arrive at your conclusions.
\end{question}
\mynewpage

\begin{question}
  Small \textit{Happy Fun Balls} have a about one-third the diameter of a large
  \textit{Happy Fun Ball}. How many small \textit{Happy Fun Balls} would it take
  to:
  \begin{enumerate}
    \item Line one edge of the room?
    \item Cover the floor?
    \item Fill the room?
  \end{enumerate}
  Answer these questions by using a \textbf{method} that is identical (except for minor modifications) to the method you described in the first problem. This modified method, should yield new answers.
  In each case, explicitly give similar explanations of what you did using words and pictures/diagrams. Moreover, explain how you used your work to arrive at your conclusions.
\end{question}
\mynewpage

\begin{question}
  Your friend and fellow student \textit{Geometry Giorgio} suggests
  that we ignore the instructions above and think in the following way:
  \begin{quote}
    Since a large \textit{Happy Fun Ball} has about three times the
    diameter of a small \textit{Happy Fun Ball,} the answers for Problem
    $2$ above should all be about three times the answers from Problem
    $1$.
  \end{quote}
\begin{center}
  \bf Is \textit{Geometry Giorgio} correct?
\end{center}
\textbf{Check your answers from Problems 1 and 2} and use them to either \textbf{validate or invalidate}
\textit{Geometry Giorgio}'s claim. Explain what you do and explain to us how your computations help determine if 
\textit{Geometry Giorgio} is in fact correct or not.
\end{question}

\end{document}
